### 2019-07-25 article/article.tex
Added a draft of the article. To be written: Evaluation; Related Work; Conclusion

\documentclass{article}
\begin{document}
\title{\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}}
\date{}
\maketitle

\section{Introduction}
(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
\subsection{Problem}
As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart these kinds of attacks effectively. However, with the increased availability of information on the web it is becoming easier to study and learn how these attacks work. The cutting edge techniques used to carry them out is mostly found on the latest scientific research papers. Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past. Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current one possible. With this being said the most relevant paper of a certain subject becomes the paper with more references to it, thus making it an obligatory read. Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient.

\subsection{Solution}
The visualization of information using graphs is a benefit for our learning process and the construction of mental conceptual maps that makes it easier for us to retain information and relate it with everything we have learned so far on a certain topic.
With BibTrek we propose a graph visualization tool and search engine with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph using Neo4J. The use of this graph is therefore useful to relate the papers and their references making the workflow of the survey process much more efficient but also enjoyable. BibTrek would permit us to start a search from a set of either authors, publication titles or keywords dynamically producing a reference graph of with the most relevant scientific papers therefore permitting us an easy navigation and understanding of the relationships between every of its nodes.

\subsection{Overview}
In BibTrek to obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications. After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of: ArXiV, DBLP and IEEEXplore. Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4J graph database all the available hosted information about either publications, institutions, authors and subjects. This graph database can also later be queried through the use of console commands to infer useful information about the state of the system. A simple example execution would follow these steps. Let us say we want to learn about the Spectre attack. We would choose the option to query one of the mentioned above libraries, choose the option to search for a publication and then type the word "Spectre" on the console terminal. After choosing the Spectre publication (written by ), the Spectre paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user. After the fact, the user can simply watch the graph visualization created by BibTrek, this way finding which papers are the most referenced and therefore understand which shall be the one that he shall tackle firstly.

\section{Related Work}
#Yet to be researched

\section{Solution}
(Sketch)
#Write a brief introduction. Maybe use the text that I used above but here instead
\subsection{Design}
The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiqutuous on modern-day computing systems. The database module uses Neo4J and requires us to have either a local or remote instance running it. The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687. The API information is retrieved and parsed in the offered JSON format option due to its lightweight format and overall flexibility. The information in the database server is addressed using Cypher queries. The application was built using the Maven tool and uses the Neo4J driver repository in order to establish a connection with the database. It also uses the JSON repository in order to properly parse the JSON information retrieved in the GET responeses coming from the server. Finally it uses the java.net package in order to establish a connection with the DBLP API, query it and retrieve the response information.

\subsection{Implementation}
At the present time BibTrek only uses the DBLP API to obtain information about the publications. In the current implementation after the user chooses one of the options available to query the database, the user inputs a publication title that is scanned and properly parsed into a DBLP API formated query to the database. The queries are done through the URL link. After the query is sucessfully processed by the DBLP database the BibTrek HTTP module retrieves the response, parses the JSON and displays the information in the user console. After choosing whichever papers are appropriate for its research the system uses its writer module writing the parsed JSON response to a properly named ".nosql" file. The information is properly parsed into a "Cypher" query in order to be stored later in the Neo4J database Every request to the database creates a ".nosql" file that is read every 5 seconds by a thread that communicates with the Neo4J server app and stores the recent written data there. These files are then moved to a "logs" folder in order not to be re-written into the database. An example of a query from our system to the database would be the following. The user chooses the option to query the system by publication title. Let us say he choses the Spectre paper. Because of this a query is properly formated "dblp.org/publ/api?q=Spectre&format=json". In this example we are querying the DBLP database to fetch us all the available Spectre publications "q=Spectre" in the JSON format "format=json". After obtaining the HTTP response and parsing its JSON format the information is displayed to the user. Here every paper with the Spectre title is shown. The user chooses one or more of the papers to add to the database. After choosing the papers the information is then parsed into a cypher query and added to a nosql file. The thread responsible with the Neo4J communication and data storage will query the nosql folder for new files. If a new file is found the most recent data is then stored in the Neo4J communication. This information can then be visually seen by the user using the Neo4J browser. Finally the Neo4J Java thread moves the most recently written file to a logs folder in order for it not to be written again.

\section{Evaluation}
#Yet to be written

\end{document}

### 2019-07-25 article/article.tex
Phrase reconstruction

@@
 \subsection{Design}
-The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiqutuous on modern-day computing systems.
+The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems.
 The database module uses Neo4J and requires us to have either a local or remote instance running it.
 The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687.
-The API information is retrieved and parsed in the offered JSON format option due to its lightweight format and overall flexibility.
-The information in the database server is addressed using Cypher queries.
-The application was built using the Maven tool and uses the Neo4J driver repository in order to establish a connection with the database.
-It also uses the JSON repository in order to properly parse the JSON information retrieved in the GET responeses coming from the server.
-Finally it uses the java.net package in order to establish a connection with the DBLP API, query it and retrieve the response information.
+The JSON format was chosen as the way to retrieve the information from the DBLP database using the API due to it being lightweight and having overall great flexibility.
+The Neo4J database is queried using "
+Cypher" which is its standard query language.
+The application was built using the Maven tool and uses the Neo4J driver and JSON maven repositories.
+Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.
 
 \subsection{Implementation}
-At the present time BibTrek only uses the DBLP API to obtain information about the publications.
-In the current implementation after the user chooses one of the options available to query the database, the user inputs a publication title that is scanned and properly parsed into a DBLP API formated query to the database.
-The queries are done through the URL link.
-After the query is sucessfully processed by the DBLP database the BibTrek HTTP module retrieves the response, parses the JSON and displays the information in the user console.
-After choosing whichever papers are appropriate for its research the system uses its writer module writing the parsed JSON response to a properly named ".nosql" file.
-The information is properly parsed into a "Cypher" query in order to be stored later in the Neo4J database Every request to the database creates a ".nosql" file that is read every 5 seconds by a thread that communicates with the Neo4J server app and stores the recent written data there.
-These files are then moved to a "logs" folder in order not to be re-written into the database.
-An example of a query from our system to the database would be the following.
-The user chooses the option to query the system by publication title.
-Let us say he choses the Spectre paper.
-Because of this a query is properly formated "dblp.org/publ/api?q=Spectre&format=json".
-In this example we are querying the DBLP database to fetch us all the available Spectre publications "q=Spectre" in the JSON format "format=json".
-After obtaining the HTTP response and parsing its JSON format the information is displayed to the user.
-Here every paper with the Spectre title is shown.
-The user chooses one or more of the papers to add to the database.
-After choosing the papers the information is then parsed into a cypher query and added to a nosql file.
-The thread responsible with the Neo4J communication and data storage will query the nosql folder for new files.
-If a new file is found the most recent data is then stored in the Neo4J communication.
-This information can then be visually seen by the user using the Neo4J browser.
-Finally the Neo4J Java thread moves the most recently written file to a logs folder in order for it not to be written again.
+At the present time, BibTrek only uses the information obtained from querying DBLP API to populate our server.
+In the current implementation after choosing one of the available options to query the database, the user inputs either an author's name or publication title that is scanned and properly parsed into a query.
+Queries are done through the composition of a specifically formatted URL link and an HTTP request.
+After the query is successfully processed by the DBLP database the JSON response is properly parsed and displayed in the terminal console.
+After choosing whichever papers are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file.
+This file will later be used to create nodes and the relationships between them in our Neo4J database.
+This file is processed by a thread that periodically searches the current folder for newly written update files and is responsible for storing this information onto the graph database.
+Once the thread has finished its update responsibilities these files are then moved to a different folder in order not to be re-written into the database.
+An example execution of a query would be the following.
+The user starts by choosing the option to query the libraries for a publication by its title.
+Let us say he chose to query the system for publications about the Spectre attack.
+Because of this a query is properly formatted in the following way: "https://dblp.org/search/publ/api/?q=Spectre&format=json".
+The "q=Spectre" parameter in the URL link means that we are querying the system for Spectre subject; "search/publ/api/" means we will be using its API and search for a publication; "&format=json" means we want the fetched data in the JSON format.
+After obtaining the HTTP response and parsing its JSON the information is then displayed to the user.
+Here every available publication about the Spectre attack is shown on the console in order for the user to choose one or more of them adding them to the Neo4J database.
+Afterwards the chosen information is then parsed into a Cypher query and stored.
+The thread responsible with the Neo4J communication and data storage will search the BibTrek file system for newly added files.
+If a new file is found the most recent data is then stored in the Neo4J database.
+The Neo4J Java thread moves the most recently written file to a different folder than the one mentioned before.
+Finally, the constructed graph can then be observed using the Neo4J browser by the user and infer useful information about the Spectre attack its authors and other related papers.
 

### 2019-07-26 article/article.tex
Evaluation and Future Work almost completed. Abstract, Related Work and Conclusion to be started

@@
 \section{Evaluation}
-#Yet to be written
+\subsection{Tests}
+We have tested our application for a vast array of author and publication queries whilst locally running Neo4J using a Lenovo T400 computer with the following specs:
+\begin{itemize}
+\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
+\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
+\item \textbf{GPU:} Intel Mobile 4 Series Chipset
+\item \textbf{RAM:} 4GB @ 1066Mhz 
+\end{itemize}
+BibTrek sucessfully proccessed and inserted all nodes and relations into the Neo4J database.
+We were able to search for any added data with ease.
+However the data retrieved from the DBLP database might present a variable number of field attributes.
+Since we are following a fixed attribute structure for our node data, some of these fields are ignored.
+Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
+\subsection{Functionalities}
+At the current moment we can choose only to retrieve data from the DBLP publication.
+Nontheless future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of them.
+Choosing the DBLP option we are able to pick whichever option suits our interests the most.
+At the current time we are able to query by author's name, author's publications and publication title.
+Once queried BibTrek presents us the data that it has been able to retrieve.
+The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4J graph database.
+The marked options are then stored on the graph with their appropriate relations.
+It is possible at any given moment to abort any of the mentioned above procedures.
+
+\section{Future Work}
+The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID.
+Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed.
+To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library.
+At the current moment only the DBLP is being used.
+Finally while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers.
+Another aspect that should be considered is the use of dynamic attributes since at the moment any block of data that is fetched has some of its attributes unused because we adhere to a fixed attribute standard when adding data to the database.
+At the current moment the only nodes being added to the database are either Authors or Publications.
+We should consider adding Universities, Companies that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader.
+It is worth being said that nodes being created ought to be the most common set of information between the way that information is being stored in the different databases that BibTrek will be using.
+Finally along with more diverse nodes, we should be using a vast array of arguments to each one of them in order to better categorize the information being added.
+Furthermore at the current moment BibTrek allows the user to add duplicated information.
+Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already.
+Finally, we are not able to query our Neo4J graph database through the terminal console.
+The work that has to be done regarding this topic is developing the option of querying the database through a user inputed choice of a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding the user research proccess.
+An example of a query would be getting the the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.
 

### 2019-07-26 article/article.tex
typos

--- 2019-07-25 article/article.tex
@@
 \section{Evaluation}
-#Yet to be written
+\subsection{Tests}
+We have tested our application for a vast array of author and publication queries whilst locally running Neo4J using a Lenovo T400 computer with the following specs:
+\begin{itemize}
+\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
+\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
+\item \textbf{GPU:} Intel Mobile 4 Series Chipset
+\item \textbf{RAM:} 4096MB @ 1066Mhz 
+\end{itemize}
+BibTrek successfully processed and inserted all nodes and relations into the Neo4J database.
+We were able to search for any added data with ease.
+However, the data retrieved from the DBLP database might present a variable number of field attributes.
+Since we are following a fixed attribute structure for our node data, some of these fields are ignored.
+Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
+\subsection{Functionalities}
+At the current moment we can choose only to retrieve data from the DBLP publication.
+Nonetheless, future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of these.
+Choosing the DBLP option we are able to pick whichever option suits our interests the most.
+At the current time we are able to query by author's name, author's publications and publication title.
+Once queried, BibTrek presents us the data that it has been able to retrieve.
+The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4J graph database.
+The marked options are then stored on the graph with their appropriate relations.
+It is possible at any given moment to abort any of the above mentioned procedures.
+
+\section{Future Work}
+The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID.
+Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed.
+To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library.
+At the current moment only the DBLP is being used.
+Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers.
+Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute standard when adding data to the database.
+At the current moment the only nodes being added to the database are either Authors or Publications.
+We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader.
+It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using.
+Finally, along with more diverse nodes, each one of them should have a vast array of arguments in order to better categorize the information being added.
+Furthermore, at the current moment BibTrek allows the user to add duplicated information.
+Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already.
+Finally, we are not able to query our Neo4J graph database through the terminal console.
+The work to be done regarding this topic is developing the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
+An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.
 

### 2019-07-26 article/article.tex
Conclusion written and done. Moving to the Related Work

@@
 \section{Introduction}
-(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
+%(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
 \subsection{Problem}
@@
 \section{Related Work}
-#Yet to be researched
+%#Yet to be researched
 
 \section{Solution}
-(Sketch)
-#Write a brief introduction. Maybe use the text that I used above but here instead
+%(Sketch)
+%#Write a brief introduction. Maybe use the text that I used above but here instead
 \subsection{Design}
@@
 Furthermore, at the current moment BibTrek allows the user to add duplicated information.
+Also, to infer better relations between the nodes already stored in the database we should use their URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each node.
+This way we can have a richer graph and understand which of the papers is the most important building block to learn about a certain subject.
 Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already.
@@
 
+\section{Conclusion}
+The BibTrek prototype the way it was implemented allows us to fully query the DBLP database and acquire diverse information about the subject matter.
+Currently it presents a fully functional rich user interface allowing the user to insert all obtained information into the Neo4J graph database.
+We are able to construct a graph with some relevant node information and the relations between these nodes being able to infer which authors wrote each paper.
+This project's potential is related with the strength of us being able to use different databases to our advantage.
+This way we would be able to add even more data and create a very complex but informative graph.
+There is also some work to be done in inferring more information than the one being currently inferred about the retrieved data from DBLP adding more nodes and attributes to the graph representation.
+Finally, we should crawl the database publications' PDF texts in order to add a relationship between publication nodes that reference one another in the database.
+
 \end{document}

### 2019-07-26 article/article.tex
Working on the Related Work section

@@
 \section{Related Work}
-%#Yet to be researched
+Some similar work has been done using both graph databases and their references. This work is listed here.
+\item \textbf{Cross Ref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications.
+BibTrek stores publications as nodes in the database and relates every available node through their references.
+While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user inputed publications that have been dynamically fetched from different libraries.
+\item \textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} is an application that using several books' BibTeX metadata and a Neo4J graph representation, through the use of user inputed cypher queries, about either the author's name or book type, reccommends us a book.
+Similarly to BibTrek a Neo4J graph representation is used after parsing a book's metadata.
+The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
+Finally, similarly to this application, BibTrek's Cypher queries are done to fetch the most referenced paper given a single author, keyword or publication title, making the scope different.
+\item \textbf{VIS - Google Scholar Citation Visualisation} is an application that is used to create a graph based on a geographic map that has information about a publication, like for example, where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map.
+While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information.
+Finally BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
+%Nao tenho a certeza deste ultimo paragrafo no entanto.
+O VIS se calhar tambem faz isto.
 

### 2019-07-26 article/article.tex
Related Work section done

@@
 \section{Related Work}
-Some similar work has been done using both graph databases and their references. This work is listed here.
+Some similar work has been done using both graph databases and their references. This work is listed here:
+\begin{itemize}
 \item \textbf{Cross Ref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications.
 BibTrek stores publications as nodes in the database and relates every available node through their references.
-While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user inputed publications that have been dynamically fetched from different libraries.
-\item \textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} is an application that using several books' BibTeX metadata and a Neo4J graph representation, through the use of user inputed cypher queries, about either the author's name or book type, reccommends us a book.
-Similarly to BibTrek a Neo4J graph representation is used after parsing a book's metadata.
+While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user input publications that have been dynamically fetched from different libraries.
+\item \textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} is an application that using several books' BibTeX metadata and a Neo4J graph representation, through the use of user input Cypher queries, about either the author's name or book type, recommends us a book.
+Similarly to BibTrek, a Neo4J graph representation is used after parsing a book's metadata.
 The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
@@
 While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information.
-Finally BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
+Finally, BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
 %Nao tenho a certeza deste ultimo paragrafo no entanto.
 O VIS se calhar tambem faz isto.
+\end{itemize}
 

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorSearch.java
code restructuring

@@ -6,7 +6,9 @@ import java.util.Scanner;
 import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
 import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
+import inesc_id.gsd.bibtrek.app.dblp.writer.AuthorDBLPNoSQLWriter;
 import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 
@@ -28,6 +30,7 @@ public class AuthorSearch extends Search {
 		AuthorJSONParser authorJSONParser;	
 		ArrayList<Object[]> tupleArrayList;
 		SearchBranch searchBranch;
+		ArrayList<Object[]> authorsList;
 				
 		authorJSONParser = new AuthorJSONParser();
 		searchBranch = new SearchBranch(this.choice, this.userInput);
@@ -45,9 +48,12 @@ public class AuthorSearch extends Search {
 		tupleArrayList = authorJSONParser.parseString();
 		if(!tupleArrayList.isEmpty()) {		
 			try {
-				searchBranch.choose(tupleArrayList);
+				authorsList = searchBranch.choose(tupleArrayList);
+				this.write(authorsList, this.choice);
 			} catch (SearchBranchException sbe) {
 				throw new AuthorSearchException("search(): could not search for author.");
+			} catch (DBLPNoSQLWriterException dblpnosqlwe) {
+				throw new AuthorSearchException("search(): could not properly begin the write operation.");
 			}
 		}		
 	}			

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/Search.java

@@ -1,5 +1,10 @@
 package inesc_id.gsd.bibtrek.app.dblp.search;
 
+import java.util.ArrayList;
+
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.http.HTTPClient;
@@ -20,7 +25,16 @@ public abstract class Search {
 					+ " the website with url: \"" + query + "\".");
 		}
 	}
-	
-	
+		
 	public abstract void search() throws Exception;
+	
+	public void write(ArrayList<Object[]> tupleArrayList, String condition) throws DBLPNoSQLWriterException {
+		DBLPNoSQLWriter dblpNoSQLWriter;
+		try {
+			dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, condition);
+			dblpNoSQLWriter.writeToFile();
+		} catch (DBLPNoSQLWriterException dblpnosqlwe) {
+			throw new DBLPNoSQLWriterException("write(): could not invoke the writer's write function...");
+		}
+	}
 }

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/SearchBranch.java

@@ -23,7 +23,9 @@ public class SearchBranch {
 		this.userInput = userInput;
 	}
 	
-	public void choose(ArrayList<Object[]> tupleArrayList) throws SearchBranchException {
+	@SuppressWarnings("unchecked")
+	public ArrayList<Object[]> choose(ArrayList<Object[]> tupleArrayList) throws SearchBranchException {
+		Object[] tuple;
 		String publicationChoice;
 		boolean exit = false;
 		
@@ -56,10 +58,11 @@ public class SearchBranch {
 			if(StringToIntegerUtils.isInteger(publicationChoice)) {
 				addedPublications = chooseIntegerCondition(publicationChoice, tupleArrayList);				
 			} else {
-				exit = chooseStringCondition(publicationChoice, tupleArrayList, addedPublications, this.choice);
-				
+				tuple = chooseStringCondition(publicationChoice, tupleArrayList, addedPublications, this.choice);
+				exit = (boolean) tuple[0];
+				addedPublications = (ArrayList<Object[]>) tuple[1];
 				if(exit) {
-					return;
+					return addedPublications;
 				}
 			}			
 		}
@@ -91,29 +94,19 @@ public class SearchBranch {
 		return addedPublications;
 	}
 	
-	private boolean chooseStringCondition(String publicationChoice, ArrayList<Object[]> tupleArrayList, ArrayList<Object[]> addedPublications, String choice) throws SearchBranchException  {				
-		DBLPNoSQLWriter dblpNoSQLWriter;
-		
-		try {
-			if(publicationChoice.equals("a")) {
-				dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, choice);
-				dblpNoSQLWriter.writeToFile();
-				return true;
-			} else if(publicationChoice.equals("es") && !addedPublications.isEmpty()) {
-				dblpNoSQLWriter = WriteConditionFactory.getWriter(addedPublications, choice);
-				dblpNoSQLWriter.writeToFile();
-				return true;
-			} else if(publicationChoice.equals("es") && addedPublications.isEmpty()) {			
-				return true;
-			} else if(publicationChoice.equals("e!")) {			
-				return true;
-			} else {
-				System.out.println("");
-				System.out.println("You must insert a valid option!");
-				return false;
-			}
-		} catch(DBLPNoSQLWriterException dblpnosqlwe) {
-			throw new SearchBranchException("choosePublicationsToAddCharacterCondition(): could not execute a valid option!");
[…]

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPClass.java
further refactorization

@@ -1,0 +1,65 @@
+package inesc_id.gsd.bibtrek.app.dblp;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPClassException;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
+
+public class DBLPClass {
+	
+	private final static String AUTHOR = "author";
+	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
+	private final static String PUBLICATION = "publication";
+	
+	
+	public static void execute(String inputCommand, Scanner userInput) throws DBLPClassException {
+		DBLPQueryCreator queryCreator;		
+		String query, authorName, publicationTitle, getRequest;		
+		AuthorSearch authorSearch;
+		AuthorsPublicationsSearch authorsPublicationsSearch;
+		PublicationSearch publicationSearch;
+		DBLPNoSQLWriter dblpNoSQLWriter;
+		ArrayList<Object[]> tupleArrayList; 
+		
+		queryCreator = new DBLPQueryCreator();                        		 
+		
+		try {
+			switch(inputCommand) {
+				case AUTHOR:
+					authorSearch = new AuthorSearch(queryCreator, userInput, AUTHOR);
+					tupleArrayList = authorSearch.search();		
+					dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, inputCommand);
+					dblpNoSQLWriter.writeToFile();
+					break;
+				case AUTHORS_PUBLICATIONS:
[…]

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPInterface.java

@@ -9,9 +9,11 @@ import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
 import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
 import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
 import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
 import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
 import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
 import inesc_id.gsd.bibtrek.app.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.exceptions.DBLPClassException;
 import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
 import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
@@ -35,14 +37,8 @@ public class DBLPInterface {
 	}
 		
 	public void display() throws DBLPInterfaceException {
-		String query, inputCommand, authorName, publicationTitle, getRequest;
-		DBLPQueryCreator queryCreator;		
-		AuthorSearch authorSearch;
-		AuthorsPublicationsSearch authorsPublicationsSearch;
-		PublicationSearch publicationSearch;
-		
-        queryCreator = new DBLPQueryCreator();                        		   
-        
+		String inputCommand;
+		          
 		while(true) {
 			System.out.println("");
 			System.out.println("(*)  : DBLP MENU");
@@ -61,16 +57,13 @@ public class DBLPInterface {
 		    try {
 				switch(inputCommand) {
 					case SEARCH_AUTHOR_BY_NAME:
-						authorSearch = new AuthorSearch(queryCreator, this.userInput, AUTHOR);
-						authorSearch.search();					
+						DBLPClass.execute(inputCommand, this.userInput);
 						break;
 					case SEARCH_AUTHORS_PUBLICATIONS:
-						authorsPublicationsSearch = new AuthorsPublicationsSearch(queryCreator, this.userInput, AUTHORS_PUBLICATIONS);
-						authorsPublicationsSearch.search();					
[…]

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorSearch.java

@@ -25,12 +25,12 @@ public class AuthorSearch extends Search {
 	}
 
 	@Override
-	public void search() throws AuthorSearchException {
+	public ArrayList<Object[]> search() throws AuthorSearchException {
 		String query, authorName, getRequest;		
 		AuthorJSONParser authorJSONParser;	
 		ArrayList<Object[]> tupleArrayList;
 		SearchBranch searchBranch;
-		ArrayList<Object[]> authorsList;
+		ArrayList<Object[]> authorsList = null;
 				
 		authorJSONParser = new AuthorJSONParser();
 		searchBranch = new SearchBranch(this.choice, this.userInput);
@@ -48,14 +48,12 @@ public class AuthorSearch extends Search {
 		tupleArrayList = authorJSONParser.parseString();
 		if(!tupleArrayList.isEmpty()) {		
 			try {
-				authorsList = searchBranch.choose(tupleArrayList);
-				this.write(authorsList, this.choice);
+				authorsList = searchBranch.choose(tupleArrayList);					
 			} catch (SearchBranchException sbe) {
 				throw new AuthorSearchException("search(): could not search for author.");
-			} catch (DBLPNoSQLWriterException dblpnosqlwe) {
-				throw new AuthorSearchException("search(): could not properly begin the write operation.");
-			}
-		}		
+			} 
+		} 
+		return authorsList;
 	}			
 	
 }

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/PublicationSearch.java

@@ -23,10 +23,10 @@ public class PublicationSearch extends Search {
 	}
 
 	@Override
-	public void search() throws PublicationSearchException {
+	public ArrayList<Object[]> search() throws PublicationSearchException {
 		String query, userChoice, getRequest;		
 		PublicationJSONParser publicationJSONParser;	
-		ArrayList<Object[]> tupleArrayList;
+		ArrayList<Object[]> tupleArrayList = null;
 		SearchBranch searchBranch;
 				
 		publicationJSONParser = new PublicationJSONParser();
@@ -54,6 +54,8 @@ public class PublicationSearch extends Search {
 				throw new PublicationSearchException("search(): could not search for publication.");
 			}			
 		}
+		
+		return tupleArrayList;
 	}
 	
 	protected void search(String title) throws PublicationSearchException {

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/Search.java

@@ -4,7 +4,6 @@ import java.util.ArrayList;
 
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
 import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.http.HTTPClient;
@@ -26,15 +25,6 @@ public abstract class Search {
 		}
 	}
 		
-	public abstract void search() throws Exception;
-	
-	public void write(ArrayList<Object[]> tupleArrayList, String condition) throws DBLPNoSQLWriterException {
-		DBLPNoSQLWriter dblpNoSQLWriter;
-		try {
-			dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, condition);
-			dblpNoSQLWriter.writeToFile();
-		} catch (DBLPNoSQLWriterException dblpnosqlwe) {
-			throw new DBLPNoSQLWriterException("write(): could not invoke the writer's write function...");
-		}
-	}
+	public abstract ArrayList<Object[]> search() throws Exception;
+
 }

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/exceptions/DBLPClassException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.exceptions;
+
+public class DBLPClassException extends SearchException {
+	
+	public DBLPClassException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public DBLPClassException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPClass.java
Restructured but need to fix bugs

@@ -21,6 +21,10 @@ public class DBLPClass {
 	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
 	private final static String PUBLICATION = "publication";
 	
+	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
+	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
+	private static final String SEARCH_PUBLICATION = "p";
+	
 	
 	public static void execute(String inputCommand, Scanner userInput) throws DBLPClassException {
 		DBLPQueryCreator queryCreator;		
@@ -30,25 +34,30 @@ public class DBLPClass {
 		PublicationSearch publicationSearch;
 		DBLPNoSQLWriter dblpNoSQLWriter;
 		ArrayList<Object[]> tupleArrayList; 
-		
+				
 		queryCreator = new DBLPQueryCreator();                        		 
 		
 		try {
 			switch(inputCommand) {
-				case AUTHOR:
+				case SEARCH_AUTHOR_BY_NAME:
 					authorSearch = new AuthorSearch(queryCreator, userInput, AUTHOR);
 					tupleArrayList = authorSearch.search();		
-					dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, inputCommand);
+					dblpNoSQLWriter = WriteConditionFactory.getWriter(tupleArrayList, AUTHOR);
 					dblpNoSQLWriter.writeToFile();
 					break;
-				case AUTHORS_PUBLICATIONS:
-					authorsPublicationsSearch = new AuthorsPublicationsSearch(queryCreator, userInput, AUTHORS_PUBLICATIONS);
-					authorsPublicationsSearch.search();					
+				case SEARCH_AUTHORS_PUBLICATIONS:
+					authorSearch = new AuthorSearch(queryCreator, userInput, AUTHOR);
+					tupleArrayList = authorSearch.search();	
+					if(tupleArrayList!=null) {
+						authorsPublicationsSearch = new AuthorsPublicationsSearch(queryCreator, userInput, AUTHORS_PUBLICATIONS);
+						authorsPublicationsSearch.search(tupleArrayList);
+					}
+					
 					break;
-				case PUBLICATION:
+				case SEARCH_PUBLICATION:
 					publicationSearch = new PublicationSearch(queryCreator, userInput, PUBLICATION);
 					tupleArrayList = publicationSearch.search();
[…]

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPInterface.java

@@ -1,30 +1,12 @@
 package inesc_id.gsd.bibtrek.app.dblp;
 
-import java.util.ArrayList;
 import java.util.Scanner;
 
-import inesc_id.gsd.bibtrek.app.http.HTTPClient;
-import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
-import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
-import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
-import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorsPublicationsSearchException;
 import inesc_id.gsd.bibtrek.app.exceptions.DBLPClassException;
 import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
-import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
 
 public class DBLPInterface {
-	
-	private final static String AUTHOR = "author";
-	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
-	private final static String PUBLICATION = "publication";
-	
+		
 	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
 	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
 	private static final String SEARCH_PUBLICATION = "p";

### 2019-07-26 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorsPublicationsSearch.java

@@ -12,7 +12,7 @@ import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
 import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 
-public class AuthorsPublicationsSearch extends Search {;
+public class AuthorsPublicationsSearch {;
 	
 	private String choice;
 	private DBLPQueryCreator queryCreator; 
@@ -25,32 +25,17 @@ public class AuthorsPublicationsSearch extends Search {;
 		this.choice = choice;
 	}
 
-	@Override
-	public void search() throws AuthorsPublicationsSearchException {
+	public void search(ArrayList<Object[]> tupleArrayList) throws AuthorsPublicationsSearchException {
 		String authorName, query, userChoice, getRequest, continueChoice;		
 		AuthorJSONParser authorJSONParser;	
-		ArrayList<Object[]> tupleArrayList, chosenAuthors;		
+		ArrayList<Object[]> chosenAuthors;		
 		SearchBranch searchBranch;
 		AuthorsPublicationsSearchBranch authorsPublicationsSearchBranch;
 		PublicationSearch publicationSearch;
 				
 		authorJSONParser = new AuthorJSONParser();
 		searchBranch = new SearchBranch(this.choice, this.userInput);
-		authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.userInput);
-		
-		System.out.print("Type the author's name: ");
-		userChoice = this.userInput.nextLine(); 
-		query = queryCreator.searchAuthorByName(userChoice);
-					
-		try {
-			getRequest = this.executeQuery(query);
-		} catch (SearchException se) {
-			throw new AuthorsPublicationsSearchException("search(): could not execute the query: \"" + query + "\".");
-		}
-		authorJSONParser.setString(getRequest);
-		System.out.println("");
-		System.out.println("(*) Authors Found: ");
-		tupleArrayList = authorJSONParser.parseString();
+		authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.userInput);						
 
 		if(!tupleArrayList.isEmpty()) {			
 			try {

### 2019-07-29 article/article.tex
using the appropriate page format
article, typos, formating

--- 2019-07-26 article/article.tex
@@
-\documentclass{article}
+\documentclass[twocolumn]{article}
+\usepackage{hyperref}
+
 \begin{document}
@@
 \maketitle
-
 \section{Introduction}
-%(Quase final. Cortar palavras. Algumas das coisas aqui podem ser usadas como introduções na solução e avaliação)
 \subsection{Problem}
@@
 Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past.
-Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current one possible.
+Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current ones possible.
 With this being said the most relevant paper of a certain subject becomes the paper with more references to it, thus making it an obligatory read.
@@
 \subsection{Solution}
-The visualization of information using graphs is a benefit for our learning process and the construction of mental conceptual maps that makes it easier for us to retain information and relate it with everything we have learned so far on a certain topic.
-With BibTrek we propose a graph visualization tool and search engine with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph using Neo4J.
+The visualization of information using graphs is a benefit for our learning process and the construction of mental conceptual maps that makes it easier for us to retain information and relate it with everything we have learned so far on a certain topic \cite{enhancinglearningwithvisualizationtechniques}.
+With BibTrek we propose a graph visualization tool and search engine with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph using Neo4j \cite{neo4j}.
 The use of this graph is therefore useful to relate the papers and their references making the workflow of the survey process much more efficient but also enjoyable.
-BibTrek would permit us to start a search from a set of either authors, publication titles or keywords dynamically producing a reference graph of with the most relevant scientific papers therefore permitting us an easy navigation and understanding of the relationships between every of its nodes.
+BibTrek would permit us to start a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers therefore permitting us an easy navigation and understanding of the relationships between every of its nodes.
 
@@
 In BibTrek to obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
-After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of: ArXiV, DBLP and IEEEXplore.
-Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4J graph database all the available hosted information about either publications, institutions, authors and subjects.
+After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
+Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j graph database all the available hosted information about either publications, institutions, authors and subjects.
 This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.
@@
 Let us say we want to learn about the Spectre attack.
-We would choose the option to query one of the mentioned above libraries, choose the option to search for a publication and then type the word "Spectre" on the console terminal.
-After choosing the Spectre publication (written by ), the Spectre paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
-After the fact, the user can simply watch the graph visualization created by BibTrek, this way finding which papers are the most referenced and therefore understand which shall be the one that he shall tackle firstly.
+We would choose the option to query one of the mentioned above libraries.
+Next, by selecting the option to search for a publication, we would then then type the word "Spectre" on the console terminal.
+After choosing the Spectre publication, the paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
+After the fact, the user can simply watch the graph visualization created by BibTrek, this way finding which papers are the most referenced and therefore understand which shall be the one that he should tackle first.
 
 \section{Related Work}
-%#Yet to be researched
+Some similar work has been done using both graph databases and an interwined network of publications' references. This work is briefly analyzed below.\\[1\baselineskip]
+\textbf{Cross Ref} \cite{crossref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications.
+BibTrek stores publications as nodes in the database and relates every available node through their references.
+While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user input publications that have been dynamically fetched from different libraries.\\[1\baselineskip]
+\textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} \cite{bookrecusingneo4j} is an application that using several books' BibTeX metadata and a Neo4j graph representation, through the use of user input Cypher queries, about either the author's name or book type, recommends us a book.
+Similarly to BibTrek, a Neo4j graph representation is used after parsing a book's metadata.
+The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
+Finally, BibTrek's Cypher queries are similarly done but to fetch the most referenced paper given a single author, keyword or publication title, making the scope different from book searching alone.\\[1\baselineskip]
+\textbf{VIS - Google Scholar Citation Visualisation} \cite{vis} is an application that is used to create a graph based on a geographic map that has information about a publication, for example, the place where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map.
+While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information from.
+Finally, BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
 
 \section{Solution}
-%(Sketch)
-%#Write a brief introduction. Maybe use the text that I used above but here instead
 \subsection{Design}
 The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems.
-The database module uses Neo4J and requires us to have either a local or remote instance running it.
-The connection of the JVM to the Neo4J is made using the BOLT protocol on the network port: 7687.
+The database module uses Neo4j and requires us to have either a local or remote instance running it.
+The connection of the JVM to the Neo4j is made using the BOLT protocol on network port 7687.
 The JSON format was chosen as the way to retrieve the information from the DBLP database using the API due to it being lightweight and having overall great flexibility.
-The Neo4J database is queried using "
-Cypher" which is its standard query language.
-The application was built using the Maven tool and uses the Neo4J driver and JSON maven repositories.
+The Neo4j database is queried using Cypher\cite{cypher} which is its standard query language.
+The application was built using the Apache Maven tool and uses the Neo4j driver and JSON maven repositories.
 Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.
@@
 After choosing whichever papers are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file.
-This file will later be used to create nodes and the relationships between them in our Neo4J database.
+This file will later be used to create nodes and the relationships between them in our Neo4j database.
 This file is processed by a thread that periodically searches the current folder for newly written update files and is responsible for storing this information onto the graph database.
@@
 Let us say he chose to query the system for publications about the Spectre attack.
-Because of this a query is properly formatted in the following way: "https://dblp.org/search/publ/api/?q=Spectre&format=json".
-The "q=Spectre" parameter in the URL link means that we are querying the system for Spectre subject; "search/publ/api/" means we will be using its API and search for a publication; "&format=json" means we want the fetched data in the JSON format.
+Because of this a query is properly formatted in the following way: \url{https://dblp.org/search/publ/api/?q=Spectre&format=json}.
+The "q=Spectre" parameter in the URL link meaning that we are querying the system for Spectre subject; "search/publ/api/" means we will be using its API and search for a publication; "&format=json" means we want the fetched data in the JSON format.
 After obtaining the HTTP response and parsing its JSON the information is then displayed to the user.
-Here every available publication about the Spectre attack is shown on the console in order for the user to choose one or more of them adding them to the Neo4J database.
-Afterwards the chosen information is then parsed into a Cypher query and stored.
-The thread responsible with the Neo4J communication and data storage will search the BibTrek file system for newly added files.
-If a new file is found the most recent data is then stored in the Neo4J database.
-The Neo4J Java thread moves the most recently written file to a different folder than the one mentioned before.
-Finally, the constructed graph can then be observed using the Neo4J browser by the user and infer useful information about the Spectre attack its authors and other related papers.
+Here, every available publication about the Spectre attack is shown on the console, in order for the user to choose one or more of them, therefore adding them to the Neo4j database.
+Afterwards, the chosen information is then parsed into a Cypher query and stored.
+The thread responsible with the Neo4j communication and data storage will search the BibTrek file system for newly added files.
+If a new file is found the most recent data is then stored in the Neo4j database.
+The Neo4j Java thread moves the most recently written file to a different folder than the one mentioned before.
+Finally, the constructed graph can then be observed using the Neo4j browser by the user and infer useful information about the Spectre attack its authors and other related papers.
 
@@
 \subsection{Tests}
-We have tested our application for a vast array of author and publication queries whilst locally running Neo4J using a Lenovo T400 computer with the following specs:
+We have tested our application for a vast array of author and publication queries whilst locally running Neo4j using a Lenovo T400 computer with the following specs:
 \begin{itemize}
@@
 \end{itemize}
-BibTrek successfully processed and inserted all nodes and relations into the Neo4J database.
+BibTrek successfully processed and inserted all nodes and relations into the Neo4j database.
 We were able to search for any added data with ease.
@@
 Once queried, BibTrek presents us the data that it has been able to retrieve.
-The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4J graph database.
+The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4j graph database.
 The marked options are then stored on the graph with their appropriate relations.
@@
 At the current moment the only nodes being added to the database are either Authors or Publications.
-We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the reader.
+We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the user.
 It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using.
@@
 Furthermore, at the current moment BibTrek allows the user to add duplicated information.
-Also, to infer better relations between the nodes already stored in the database we should use their URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each node.
+Also, to infer better relations between the nodes already stored in the database we should use their URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each.
 This way we can have a richer graph and understand which of the papers is the most important building block to learn about a certain subject.
 Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already.
-Finally, we are not able to query our Neo4J graph database through the terminal console.
-The work to be done regarding this topic is developing the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
+Finally, we are not able to query our Neo4j graph database through the terminal console.
+The work to be done regarding this topic, is the development of the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
 An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.
@@
 The BibTrek prototype the way it was implemented allows us to fully query the DBLP database and acquire diverse information about the subject matter.
-Currently it presents a fully functional rich user interface allowing the user to insert all obtained information into the Neo4J graph database.
-We are able to construct a graph with some relevant node information and the relations between these nodes being able to infer which authors wrote each paper.
-This project's potential is related with the strength of us being able to use different databases to our advantage.
+Currently it presents a fully functional rich user interface allowing the user to insert all obtained information into the Neo4j graph database.
+We are able to construct a graph with some relevant node information.
+This information being authors and publications and the relations between them therefore being able to infer which authors wrote each paper.
+BibTrek's main potential is the strength of us being able to use different databases to our advantage.
 This way we would be able to add even more data and create a very complex but informative graph.
-There is also some work to be done in inferring more information than the one being currently inferred about the retrieved data from DBLP adding more nodes and attributes to the graph representation.
-Finally, we should crawl the database publications' PDF texts in order to add a relationship between publication nodes that reference one another in the database.
+There is also some work to be done in inferring more information than the one being currently inferred about the retrieved data from DBLP, adding more nodes and attributes to the graph representation.
+Finally, we should crawl the database publications' PDF texts in order for us to add a relationship between publication nodes that reference one another in the database.
+
+\begin{thebibliography}{9}
+
+\bibitem{enhancinglearningwithvisualizationtechniques} 
+J. Klerkx, K. Verbert, E. Duval,
+\textit{Learning with Visualization Techniques}, 2014.
+In: J. Spector, M. Merrill, J. Elen, M. Bishop 
+\textit{Handbook of Research on Educational Communications and Technology}. 
+Springer, New York, New York.
+
+\bibitem{neo4j} 
+Neo4j 2019, 
+\textit{Neo4j Graph Platform – The Leader in Graph Databases}, 
+Neo4j, viewed 29 July 2019, 
+\url{https://neo4j.com}
+
+\bibitem{arxiv}
+arXiv 2019,
+\textit{arXiv API | arXiv e-print repository},
+arXiv, viewed 29 July 2019,
+\url{https://arxiv.org/help/api}
+
+\bibitem{dblp}
+dblp 2019,
+\textit{How to use the dblp search API? - dblp},
+dblp, viewed 29 July 2019,
+\url{https://dblp.uni-trier.de/faq/How+to+use+the+dblp+search+API}
+
+\bibitem{ieeexplore}
+IEEE Xplore 2019,
+\textit{IEEE Xplore API},
+IEEE Xplore, viewed 29 July 2019,
+\url{https://developer.ieee.org}
+
+\bibitem{crossref}
+Crossref 2019,
+\textit{You are Crossref - Crossref},
+Crossref, viewed 29 July 2019,
+\url{https://www.crossref.org/}
+
+\bibitem{bookrecusingneo4j}
+I. N. P. W. Dharmawan and R. Sarno, 
+\textit{Book recommendation using Neo4j graph database in BibTeX book metadata}, 2017.
+In: 3rd International Conference on Science in Information Technology (ICSITech). 
+Bandung, Indonesia.
+
+\bibitem{vis}
+C. Yang, I. Todd, L. Sanby, 2019,
+\textit{Google Scholar Citation Visualisation},
+Google Scholar Citation Visualisation, viewed 29 July 2019,
+\url{https://people.cs.uct.ac.za/~yngcha005/vis2015/index.html}
+
+\bibitem{cypher}
+Neo4j 2019,
+\textit{Cypher Query Language - Neo4j},
+Neo4j, viewed 29 July 2019,
+\url{https://neo4j.com/developer/cypher-query-language/}
+
+\end{thebibliography}
 

### 2019-07-29 article/article.tex
Added Acknowledgement section to the article

@@
 
+\section{Acknowledgements}
+The writer of this article would like to thank Professor Miguel L.
+Pardal and INESC-ID for having invited him for a one month summer-internship program.
+With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers.
+Non only that but also acquired a greater  work from  and has the utmost gratitude for having been part of this project from which he has learned immensely from.
+
 \begin{thebibliography}{9}

### 2019-07-29 article/article.tex
Added the abstract

@@
 \date{}
+\author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico}
+\date{2019\\ August}
 \maketitle
+
+\textbf{\textit{Abstract}--With the advent of bigger and more elaborate cyberattacks the search for hackers with a deep understanding of the most recent cutting-edge attacks is becoming more difficult.
+Since the information about these techniques is present in the most recent scientific research publications and because most of the knowledge present in them is built onto the work of several other publications, which they reference, we present BibTrek, a Graph Visualization Tool and Search Engine for Cybersecurity Papers, that intends to solve this exact problem.
+With BibTrek we shall make use of several computer science web-based libraries to acquire information from multiple sources and display them into a Neo4j graph database to better relate the references between publications, but also authors and other relevant information for the reader.
+We then present the implementation of a simple command line program that allows us to query the API of DBLP and select which information we shall include on our database.
+Finally, we talk about further considerations and engineering developments in order for BibTrek to provide a more complex and richer functioning yet providing an easy and enjoyable experience for the user.}
+
+\\[1\baselineskip]
+
 \section{Introduction}
@@
 With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers.
-Non only that but also acquired a greater  work from  and has the utmost gratitude for having been part of this project from which he has learned immensely from.
+Non only that but also acquired a greater work ethic.
+With this being said he has the utmost gratitude for having been part of this project from which he has learned immensely from.
 

### 2019-07-30 article/article.tex
Restructuring of the article

@@
 \begin{document}
-\title{\textbf{BibTrek Prototype: A Graph Visualization Tool and Search Engine for Cybersecurity Papers}}
+\title{\textbf{BibTrek: A Graph Visualization Tool for Cybersecurity Publications}}
 \date{}
 \author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico}
-\date{2019\\ August}
+\date{2019\\ July}
 \maketitle
@@
 \section{Introduction}
+
+The number of cyberattacks is on the rise.
+The CVE statistics \cite{cvestatisticsbyyear} show a 21.56\% increase in the number of documented vulnerabilities over the past 19 years.
+With the amount of information available it is very easy for an ill-intentioned individual to carry out an attack and exploit some system with minimal computacional resources.
+
 \subsection{Problem}
@@
 However, with the increased availability of information on the web it is becoming easier to study and learn how these attacks work.
-The cutting edge techniques used to carry them out is mostly found on the latest scientific research papers.
+The techniques used to carry them out are are mostly found in blog posts and other social media with short publication times.
+However, for in-depth analysis and scientic rigour, there are scientific publications in peer-reviewed conferences and journals.
 Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past.
-Because of this, to understand the most recent concepts it is important the reading of the referenced papers that made the writing of the current ones possible.
-With this being said the most relevant paper of a certain subject becomes the paper with more references to it, thus making it an obligatory read.
-Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient.
+Because of this, to understand the most recent concepts it is important to read the referenced papers that made the writing of the current ones possible.
+Usually the most cited papers are the most relevant regarding a certain subject.
+Having said that, the reality is that performing these kinds of bibliography surveys are time-consuming and inefficient, thus, creating the possibility of them being improved upon.
 
 \subsection{Solution}
-The visualization of information using graphs is a benefit for our learning process and the construction of mental conceptual maps that makes it easier for us to retain information and relate it with everything we have learned so far on a certain topic \cite{enhancinglearningwithvisualizationtechniques}.
-With BibTrek we propose a graph visualization tool and search engine with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph using Neo4j \cite{neo4j}.
-The use of this graph is therefore useful to relate the papers and their references making the workflow of the survey process much more efficient but also enjoyable.
-BibTrek would permit us to start a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers therefore permitting us an easy navigation and understanding of the relationships between every of its nodes.
-
-\subsection{Overview}
-In BibTrek to obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
-After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
-Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j graph database all the available hosted information about either publications, institutions, authors and subjects.
-This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.
+The visualization of information using graphs has the potential to improve the learning process and the construction of conceptual mind maps that make it easier to retain information and relate it with other topics \cite{enhancinglearningwithvisualizationtechniques}.
+With BibTrek we propose a graph visualization tool with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph.
+The use of this graph is therefore useful to relate the papers and their references making the workflow of the survey process more efficient.
+We implemented a tool prototype.
+It allows a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers therefore permitting an easy navigation of information.
 A simple example execution would follow these steps.
@@
 We would choose the option to query one of the mentioned above libraries.
-Next, by selecting the option to search for a publication, we would then then type the word "Spectre" on the console terminal.
+Next, by selecting the option to search for a publication, we would then then type the word ``Spectre`` on the console terminal.
 After choosing the Spectre publication, the paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
@@
 
-\section{Related Work}
-Some similar work has been done using both graph databases and an interwined network of publications' references. This work is briefly analyzed below.\\[1\baselineskip]
-\textbf{Cross Ref} \cite{crossref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications.
-BibTrek stores publications as nodes in the database and relates every available node through their references.
-While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user input publications that have been dynamically fetched from different libraries.\\[1\baselineskip]
-\textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} \cite{bookrecusingneo4j} is an application that using several books' BibTeX metadata and a Neo4j graph representation, through the use of user input Cypher queries, about either the author's name or book type, recommends us a book.
-Similarly to BibTrek, a Neo4j graph representation is used after parsing a book's metadata.
-The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
-Finally, BibTrek's Cypher queries are similarly done but to fetch the most referenced paper given a single author, keyword or publication title, making the scope different from book searching alone.\\[1\baselineskip]
-\textbf{VIS - Google Scholar Citation Visualisation} \cite{vis} is an application that is used to create a graph based on a geographic map that has information about a publication, for example, the place where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map.
-While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information from.
-Finally, BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
+\subsection{Overview}
+In section 2 we present the solution design and implementation.
+In section 3 we present an evaluation of the results and functionalities of BibTrek.
+In section 4 we show related work from other authors.
+In section 5 we discuss further developments and upgrades to the application.
+Finally, in section 6 we present a brief conclusion of the work presented in the previous sections.
+\\[1\baselineskip]
 
 \section{Solution}
+
+In this section we present the design and implementation of the BibTrek prototype.
+Here we discuss the use of the software that was used for the design of the application and the reasoning behind its choice.
+We also go in depth about the specifics of the implementation including the communication protocol, data parsing, access and storage.
+
 \subsection{Design}
@@
 Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.
+\\[1\baselineskip]
+To obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
+After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
+We present the results of the surveyed publicly-available bibliographic APIs in Table 1.
+Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j\cite{neo4j} graph database all the available hosted information about either publications, institutions, authors and subjects.
+This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.
+
+\begin{table}[]
+\centering
+\captionof{\textbf{Table 1}}
+\\[1\baselineskip]
+\begin{tabular}{c|c|c|c|}
+\centering
+\cline{2-4}
+\multicolumn{1}{l|}{}                     & API & Crawlers & Key \\ \hline
+\multicolumn{1}{|c|}{ACM Digital Library} & No  & No       & N/A \\ \hline
+\multicolumn{1}{|c|}{ArXiV}               & Yes & Yes      & No  \\ \hline
+\multicolumn{1}{|c|}{DBLP}                & Yes & Yes      & No  \\ \hline
+\multicolumn{1}{|c|}{Google Scholar}      & No  & No       & N/A \\ \hline
+\multicolumn{1}{|c|}{IEEEXplore}          & Yes & No       & Yes \\ \hline
+\end{tabular}
+\end{table}
 
@@
 After the query is successfully processed by the DBLP database the JSON response is properly parsed and displayed in the terminal console.
-After choosing whichever papers are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file.
+After choosing whichever publications are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file.
 This file will later be used to create nodes and the relationships between them in our Neo4j database.
@@
 Because of this a query is properly formatted in the following way: \url{https://dblp.org/search/publ/api/?q=Spectre&format=json}.
-The "q=Spectre" parameter in the URL link meaning that we are querying the system for Spectre subject; "search/publ/api/" means we will be using its API and search for a publication; "&format=json" means we want the fetched data in the JSON format.
+The ``q=Spectre`` parameter in the URL link meaning that we are querying the system for Spectre subject; ``search/publ/api/`` means we will be using its API and search for a publication; ``&format=json`` means we want the fetched data in the JSON format.
 After obtaining the HTTP response and parsing its JSON the information is then displayed to the user.
@@
 Afterwards, the chosen information is then parsed into a Cypher query and stored.
-The thread responsible with the Neo4j communication and data storage will search the BibTrek file system for newly added files.
+The thread responsible for the Neo4j communication and data storage will search the BibTrek file system for newly added files.
 If a new file is found the most recent data is then stored in the Neo4j database.
@@
 \subsection{Tests}
-We have tested our application for a vast array of author and publication queries whilst locally running Neo4j using a Lenovo T400 computer with the following specs:
+We have tested our application for a set of author and publication queries whilst locally running Neo4j using a computer with the following specs:
 \begin{itemize}
@@
 The marked options are then stored on the graph with their appropriate relations.
-It is possible at any given moment to abort any of the above mentioned procedures.
+It is possible at any given moment to cancel any of the above mentioned procedures.
+
+\section{Related Work}
+Some similar work has been done using both graph databases and an interwined network of publications' references. This work is briefly analyzed below.\\[1\baselineskip]
+\textbf{Cross Ref} \cite{crossref} is a platform on which the registered publishers are given the option to store and relate their publication references with other available database publications.
+BibTrek stores publications as nodes in the database and relates every available node through their references.
+While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user input publications that have been dynamically fetched from different libraries.\\[1\baselineskip]
+\textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} \cite{bookrecusingneo4j} is an application that using several books' BibTeX metadata and a Neo4j graph representation, through the use of user input Cypher queries, about either the author's name or book type, recommends us a book.
+Similarly to BibTrek, a Neo4j graph representation is used after parsing a book's metadata.
+The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
+Finally, BibTrek's Cypher queries are similarly done but to fetch the most referenced paper given a single author, keyword or publication title, making the scope different from book searching alone.\\[1\baselineskip]
+\textbf{VIS - Google Scholar Citation Visualisation} \cite{vis} is an application that is used to create a graph based on a geographic map that has information about a publication, for example, the place where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map.
+While BibTrek does not use a map representation, on the other hand, unlike VIS, that only uses Google Scholar, BibTrek uses different libraries to fetch its information from.
+Finally, BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
 
 \section{Future Work}
-The reader of this article has to keep in mind that this project was developed in one month throughout the writer's internship with INESC-ID.
-Because of this there are many aspects of the current BibTrek implementation that ought to be further engineered and developed.
-To begin with, one of the obvious aspects to further develop would be to fetch information from more than one web based library.
+The current version of this project was developed in one person-month.
+Because of this there are many aspects of the current BibTrek implementation that can be further engineered and developed.
+To begin data can be fetched from more than one web based library.
 At the current moment only the DBLP is being used.
 Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers.
-Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute standard when adding data to the database.
-At the current moment the only nodes being added to the database are either Authors or Publications.
+Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute schema when adding data to the database.
+In the current version the nodes being added to the database are either Authors or Publications.
 We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the user.
-It is worth being said that nodes being created ought to be the most common set of information between the data that is being stored in the different databases that BibTrek will be using.
-Finally, along with more diverse nodes, each one of them should have a vast array of arguments in order to better categorize the information being added.
-Furthermore, at the current moment BibTrek allows the user to add duplicated information.
-Also, to infer better relations between the nodes already stored in the database we should use their URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each.
+The BibTrek data schema should be developed to be able to represent a ``union'' of the most popular bibliographic databases.
+Furthermore, in the current version BibTrek allows the user to add duplicated information.
+\\[1\baselineskip]
+Another key aspect to develop is the ability to infer better relations between the nodes already stored in the database.
+With this point in mind, we should use the node's URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each.
 This way we can have a richer graph and understand which of the papers is the most important building block to learn about a certain subject.
-Obviously a check should be added in the Java code that compares if the information that is trying to be added has been put there already.
-Finally, we are not able to query our Neo4j graph database through the terminal console.
+Again, information that is trying to be added must be compared with the one that has been put there already.
+Finally, we are not able to query our Neo4j graph database through the terminal console, apart from the example module, since there was not enough time to implement it in the current version of the system.
 The work to be done regarding this topic, is the development of the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
@@
 \section{Conclusion}
-The BibTrek prototype the way it was implemented allows us to fully query the DBLP database and acquire diverse information about the subject matter.
-Currently it presents a fully functional rich user interface allowing the user to insert all obtained information into the Neo4j graph database.
+This paper describes the BibTrek prototype that was implemented.
+It allows us to fully query the DBLP database and acquire diverse information about the subject matter.
+Currently it presents a fully functional user interface allowing the user to insert all obtained information into the Neo4j graph database.
 We are able to construct a graph with some relevant node information.
-This information being authors and publications and the relations between them therefore being able to infer which authors wrote each paper.
-BibTrek's main potential is the strength of us being able to use different databases to our advantage.
+Namely authors and publications and the relations between them.
+BibTrek's main potential is the simplification of an exploratory bibliographic database to our advantage.
 This way we would be able to add even more data and create a very complex but informative graph.
 There is also some work to be done in inferring more information than the one being currently inferred about the retrieved data from DBLP, adding more nodes and attributes to the graph representation.
-Finally, we should crawl the database publications' PDF texts in order for us to add a relationship between publication nodes that reference one another in the database.
 
@@
 \begin{thebibliography}{9}
+
+\bibitem{cvestatisticsbyyear}
+CVE 2019,
+\textit{Browse cve vulnerabilities by date - CVE Details},
+CVE, viewed 30 July 2019,
+\url{https://www.cvedetails.com/browse-by-date.php}
 

### 2019-07-30 article/article.tex
More restructuring

@@
 
-\\[1\baselineskip]
-
 \section{Introduction}
@@
 With the amount of information available it is very easy for an ill-intentioned individual to carry out an attack and exploit some system with minimal computacional resources.
-
-\subsection{Problem}
+\\[1\baselineskip]
 As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart these kinds of attacks effectively.
@@
 It allows a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers therefore permitting an easy navigation of information.
+
+\subsection{Example}
 A simple example execution would follow these steps.
@@
 \begin{tabular}{c|c|c|c|}
-\centering
 \cline{2-4}
@@
 
+\bibitem{arxiv}
+arXiv 2019,
+\textit{arXiv API | arXiv e-print repository},
+arXiv, viewed 29 July 2019,
+\url{https://arxiv.org/help/api}
+
+\bibitem{crossref}
+Crossref 2019,
+\textit{You are Crossref - Crossref},
+Crossref, viewed 29 July 2019,
+\url{https://www.crossref.org/}
+
 \bibitem{cvestatisticsbyyear}
@@
 \url{https://www.cvedetails.com/browse-by-date.php}
+
+\bibitem{bookrecusingneo4j}
+I. N. P. W. Dharmawan and R. Sarno, 
+\textit{Book recommendation using Neo4j graph database in BibTeX book metadata}, 2017.
+In: 3rd International Conference on Science in Information Technology (ICSITech). 
+Bandung, Indonesia.
+
+\bibitem{cypher}
+Neo4j 2019,
+\textit{Cypher Query Language - Neo4j},
+Neo4j, viewed 29 July 2019,
+\url{https://neo4j.com/developer/cypher-query-language/}
+
+\bibitem{dblp}
+dblp 2019,
+\textit{How to use the dblp search API? - dblp},
+dblp, viewed 29 July 2019,
+\url{https://dblp.uni-trier.de/faq/How+to+use+the+dblp+search+API}
+
+\bibitem{ieeexplore}
+IEEE Xplore 2019,
+\textit{IEEE Xplore API},
+IEEE Xplore, viewed 29 July 2019,
+\url{https://developer.ieee.org}
 
@@
 
-\bibitem{arxiv}
-arXiv 2019,
-\textit{arXiv API | arXiv e-print repository},
-arXiv, viewed 29 July 2019,
-\url{https://arxiv.org/help/api}
-
-\bibitem{dblp}
-dblp 2019,
-\textit{How to use the dblp search API? - dblp},
-dblp, viewed 29 July 2019,
-\url{https://dblp.uni-trier.de/faq/How+to+use+the+dblp+search+API}
-
-\bibitem{ieeexplore}
-IEEE Xplore 2019,
-\textit{IEEE Xplore API},
-IEEE Xplore, viewed 29 July 2019,
-\url{https://developer.ieee.org}
-
-\bibitem{crossref}
-Crossref 2019,
-\textit{You are Crossref - Crossref},
-Crossref, viewed 29 July 2019,
-\url{https://www.crossref.org/}
-
-\bibitem{bookrecusingneo4j}
-I. N. P. W. Dharmawan and R. Sarno, 
-\textit{Book recommendation using Neo4j graph database in BibTeX book metadata}, 2017.
-In: 3rd International Conference on Science in Information Technology (ICSITech). 
-Bandung, Indonesia.
-
 \bibitem{vis}
@@
 
-\bibitem{cypher}
-Neo4j 2019,
-\textit{Cypher Query Language - Neo4j},
-Neo4j, viewed 29 July 2019,
-\url{https://neo4j.com/developer/cypher-query-language/}
-
 \end{thebibliography}

### 2019-07-30 article/article.tex
Article completely restructured

@@
 \section{Evaluation}
+In this section we discuss the tests that were done using the application to query a web based library and the parsing and processing of the results.
+Furthermore we elaborate on the functionalities present in BibTrek.
+Finally, we list the commands available on the program's terminal console.
+
 \subsection{Tests}
@@
 It is possible at any given moment to cancel any of the above mentioned procedures.
+\subsection{Command-line interface}
+Here we present a detailed functioning of the interface. We elaborate on every avaible option for the user to interact with, and explain the way the system interacts with the web based library.
+\\[1\baselineskip]
+Once the application is started we are presented with the choice of either selecting the option to query the DBLP database or exit the program.
+Once the first is chosen, it is presented to us the available options to query the database.
+These options are the following:
+
+\begin{itemize}
+\item \textbf{Query by author}.
+Choosing it, we are required to type the name of the author we want to search.
+Afterwards BibTrek fetches us, all authors present in the DBLP database with a similar name to the one that we have inserted previously.
+We are then told to pick which of the fetched authors we want to insert into the database.
+\item \textbf{Query by publication's title.}.
+Here, we type the title of the publication we want to find.
+After querying DBLP, we are presented with all the available publications bearing a similar title.
+We are then required to pick which of the displayed publications we want to add to our local database.
+\item \textbf{Query by author's publication}.
+Similar to the first option, we type the author's name.
+BibTrek then fetches us all the available authors in the system.
+We are then asked to choose which of the fetched authors we want to search publications of.
+After doing so, the system fetches us all the available publications for the chosen authors incrementally.
+Finally, we are required to choose which of the displayed publications we want to insert into the system
+\end{itemize}
+It is worth mentioning that any given step of the above procedures we can choose either the option of adding all the displayed information to our data set or exit the current state of the system.
 
@@
 The writer of this article would like to thank Professor Miguel L.
-Pardal and INESC-ID for having invited him for a one month summer-internship program.
+Pardal and INESC-ID for having invited him for a one month summer-internship program and for the reviewing of this article.
 With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers.

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPClass.java
File restructuring

@@ -3,17 +3,17 @@ package inesc_id.gsd.bibtrek.app.dblp;
 import java.util.ArrayList;
 import java.util.Scanner;
 
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
 import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
 import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
 import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
 import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorsPublicationsSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPClassException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
 
 public class DBLPClass {
 	
@@ -51,8 +51,7 @@ public class DBLPClass {
 					if(tupleArrayList!=null) {
 						authorsPublicationsSearch = new AuthorsPublicationsSearch(queryCreator, userInput, AUTHORS_PUBLICATIONS);
 						authorsPublicationsSearch.search(tupleArrayList);
-					}
-					
+					}					
 					break;
 				case SEARCH_PUBLICATION:
 					publicationSearch = new PublicationSearch(queryCreator, userInput, PUBLICATION);

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPInterface.java

@@ -2,8 +2,8 @@ package inesc_id.gsd.bibtrek.app.dblp;
 
 import java.util.Scanner;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPClassException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
 
 public class DBLPInterface {
 		

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPQueryCreator.java

@@ -1,6 +1,6 @@
 package inesc_id.gsd.bibtrek.app.dblp;
 
-import inesc_id.gsd.bibtrek.app.sanitizer.DBLPSanitizer;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPSanitizer;
 
 public class DBLPQueryCreator {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorSearchException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class AuthorSearchException extends SearchException {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorsPublicationsSearchException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class AuthorsPublicationsSearchException extends SearchException {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPClassException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class DBLPClassException extends SearchException {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPConnectNeo4JException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class DBLPConnectNeo4JException extends Exception {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPInterfaceException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class DBLPInterfaceException extends Exception {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPNoSQLWriterException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class DBLPNoSQLWriterException extends Exception {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPSanitizer.java

@@ -1,4 +1,6 @@
-package inesc_id.gsd.bibtrek.app.sanitizer;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+import inesc_id.gsd.bibtrek.app.sanitizer.QuerySanitizer;
 
 public class DBLPSanitizer extends QuerySanitizer {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/PublicationSearchException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class PublicationSearchException extends SearchException {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/SearchBranchException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class SearchBranchException extends Exception {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/SearchException.java

@@ -1,4 +1,4 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
 
 public class SearchException extends Exception {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorSearch.java

@@ -4,13 +4,13 @@ import java.util.ArrayList;
 import java.util.Scanner;
 
 import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
 import inesc_id.gsd.bibtrek.app.dblp.writer.AuthorDBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 
 public class AuthorSearch extends Search {
 	

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorsPublicationsSearch.java

@@ -4,13 +4,13 @@ import java.util.ArrayList;
 import java.util.Scanner;
 
 import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.AuthorsPublicationsSearchBranch;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
-import inesc_id.gsd.bibtrek.app.exceptions.AuthorsPublicationsSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 
 public class AuthorsPublicationsSearch {;
 	
@@ -25,54 +25,13 @@ public class AuthorsPublicationsSearch {;
 		this.choice = choice;
 	}
 
-	public void search(ArrayList<Object[]> tupleArrayList) throws AuthorsPublicationsSearchException {
-		String authorName, query, userChoice, getRequest, continueChoice;		
-		AuthorJSONParser authorJSONParser;	
-		ArrayList<Object[]> chosenAuthors;		
-		SearchBranch searchBranch;
-		AuthorsPublicationsSearchBranch authorsPublicationsSearchBranch;
-		PublicationSearch publicationSearch;
-				
-		authorJSONParser = new AuthorJSONParser();
-		searchBranch = new SearchBranch(this.choice, this.userInput);
-		authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.userInput);						
+	public void search(ArrayList<Object[]> tupleArrayList) throws AuthorsPublicationsSearchException {		
+		AuthorsPublicationsSearchBranch authorsPublicationsSearchBranch;										
 
 		if(!tupleArrayList.isEmpty()) {			
-			try {
[…]

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/PublicationSearch.java

@@ -4,11 +4,11 @@ import java.util.ArrayList;
 import java.util.Scanner;
 
 import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.dblp.parsing.PublicationJSONParser;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
-import inesc_id.gsd.bibtrek.app.exceptions.PublicationSearchException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 
 public class PublicationSearch extends Search {
 	
@@ -58,7 +58,7 @@ public class PublicationSearch extends Search {
 		return tupleArrayList;
 	}
 	
-	protected void search(String title) throws PublicationSearchException {
+	public void search(String title) throws PublicationSearchException {
 		String query, userChoice, getRequest;		
 		PublicationJSONParser publicationJSONParser;	
 		ArrayList<Object[]> tupleArrayList;

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/Search.java

@@ -2,10 +2,10 @@ package inesc_id.gsd.bibtrek.app.dblp.search;
 
 import java.util.ArrayList;
 
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
 import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
 import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchException;
 import inesc_id.gsd.bibtrek.app.http.HTTPClient;
 
 public abstract class Search {

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/AuthorsPublicationsSearchBranch.java

@@ -3,92 +3,55 @@ package inesc_id.gsd.bibtrek.app.dblp.search.condition;
 import java.util.ArrayList;
 import java.util.Scanner;
 
-import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
 import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
 
 public class AuthorsPublicationsSearchBranch {
 	
+	private String choice;
+	private DBLPQueryCreator queryCreator;
 	private Scanner userInput;
 	
-	public AuthorsPublicationsSearchBranch(Scanner userInput) {
+	public AuthorsPublicationsSearchBranch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {
+		this.choice = choice;
+		this.queryCreator = queryCreator;
 		this.userInput = userInput;
 	}
 	
-	public ArrayList<Object[]> choose(ArrayList<Object[]> tupleArrayList) throws SearchBranchException {
-		ArrayList<Object[]> chosenAuthors;
-		String authorChoice;
-		Object[] exitTuple;
-		boolean exit = false;
+	public void choose(ArrayList<Object[]> tupleArrayList) throws PublicationSearchException {
+		String authorName, continueChoice;
+		PublicationSearch publicationSearch;
 		
-		ArrayList<Object[]> addedAuthors = new ArrayList<Object[]>();
-		while(true) {
-							
-			System.out.println("(*) Author's Menu");			
-			System.out.println("");
-			System.out.println("(a)");
-			System.out.println("- Add all of the available choices and exits the menu ; ");
-			System.out.println("");
-			System.out.println("(es)");
-			System.out.println("- Exits the choice menu and saves the configuration you have chosen ;");
-			System.out.println("");
-			System.out.println("(e!)");
-			System.out.println("- Exits the choice menu without saving ;");
-			System.out.println(""); 
-			System.out.print("Pick one of the publications to insert in the database: ");	            									
-			authorChoice = this.userInput.nextLine();
-
-			if(StringToIntegerUtils.isInteger(authorChoice)) {
[…]

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/SearchBranch.java

@@ -3,10 +3,10 @@ package inesc_id.gsd.bibtrek.app.dblp.search.condition;
 import java.util.ArrayList;
 import java.util.Scanner;
 
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
 import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPConnectNeo4JException;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.exceptions.SearchBranchException;
 import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
 
 public class SearchBranch {

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/AuthorDBLPNoSQLWriter.java

@@ -6,7 +6,7 @@ import java.io.IOException;
 import java.util.ArrayList;
 import java.util.Iterator;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
 
 public class AuthorDBLPNoSQLWriter extends DBLPNoSQLWriter{

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/DBLPNoSQLWriter.java

@@ -2,7 +2,7 @@ package inesc_id.gsd.bibtrek.app.dblp.writer;
 
 import java.util.ArrayList;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
 
 public abstract class DBLPNoSQLWriter {

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/PublicationsDBLPNoSQLWriter.java

@@ -6,7 +6,7 @@ import java.io.IOException;
 import java.util.ArrayList;
 import java.util.Iterator;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
 import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
 
 public class PublicationsDBLPNoSQLWriter extends DBLPNoSQLWriter{

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/main/MainInterface.java

@@ -3,7 +3,7 @@ package inesc_id.gsd.bibtrek.app.main;
 import java.util.Scanner;
 
 import inesc_id.gsd.bibtrek.app.dblp.DBLPInterface;
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
 import inesc_id.gsd.bibtrek.app.exceptions.MainInterfaceException;
 
 public class MainInterface {

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/neo4j/ConnectNeo4J.java

@@ -1,7 +1,5 @@
 package inesc_id.gsd.bibtrek.app.neo4j;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPConnectNeo4JException;
-
 import org.neo4j.driver.v1.AuthTokens;
 import org.neo4j.driver.v1.Driver;
 import org.neo4j.driver.v1.GraphDatabase;
@@ -9,6 +7,8 @@ import org.neo4j.driver.v1.Session;
 import org.neo4j.driver.v1.StatementResult;
 import org.neo4j.driver.v1.Transaction;
 import org.neo4j.driver.v1.TransactionWork;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
 
 import static org.neo4j.driver.v1.Values.parameters;
 

### 2019-07-30 app/app/src/main/java/inesc_id/gsd/bibtrek/app/neo4j/WriteNeo4JThread.java

@@ -5,7 +5,7 @@ import java.util.ArrayList;
 
 import org.neo4j.driver.v1.exceptions.ServiceUnavailableException;
 
-import inesc_id.gsd.bibtrek.app.exceptions.DBLPConnectNeo4JException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
 import inesc_id.gsd.bibtrek.app.exceptions.WriteNeo4JThreadException;
 import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
 

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPClass.java
filesystem

@@ -1,0 +1,73 @@
+package inesc_id.gsd.bibtrek.app.dblp;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+
+public class DBLPClass {
+	
+	private final static String AUTHOR = "author";
+	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
+	private final static String PUBLICATION = "publication";
+	
+	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
+	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
+	private static final String SEARCH_PUBLICATION = "p";
+	
+	
+	public static void execute(String inputCommand, Scanner userInput) throws DBLPClassException {
+		DBLPQueryCreator queryCreator;		
+		String query, authorName, publicationTitle, getRequest;		
+		AuthorSearch authorSearch;
+		AuthorsPublicationsSearch authorsPublicationsSearch;
+		PublicationSearch publicationSearch;
+		DBLPNoSQLWriter dblpNoSQLWriter;
+		ArrayList<Object[]> tupleArrayList; 
+				
+		queryCreator = new DBLPQueryCreator();                        		 
+		
+		try {
+			switch(inputCommand) {
+				case SEARCH_AUTHOR_BY_NAME:
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPInterface.java

@@ -1,0 +1,64 @@
+package inesc_id.gsd.bibtrek.app.dblp;
+
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
+
+public class DBLPInterface {
+		
+	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
+	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
+	private static final String SEARCH_PUBLICATION = "p";
+	private final static String EXIT = "e";	
+	
+	private Scanner userInput;
+	
+	public DBLPInterface(Scanner userInput) {
+		this.userInput = userInput; 		
+	}
+		
+	public void display() throws DBLPInterfaceException {
+		String inputCommand;
+		          
+		while(true) {
+			System.out.println("");
+			System.out.println("(*)  : DBLP MENU");
+			System.out.println("");
+		    System.out.println("(a)  : Searches for an author by name ;");
+		    System.out.println("(ap) : Searches for an author's publications by name ;");
+		    System.out.println("(p)  : Searches for a publications by title ;");
+		    System.out.println("(e)  : Exits the DBLP query menu ;");
+		    System.out.println("");
+		    System.out.print("Type one of the above commands: ");
+		    
+		    inputCommand = this.userInput.nextLine();
+		    
+		    System.out.println("");
+		    
+		    try {
+				switch(inputCommand) {
+					case SEARCH_AUTHOR_BY_NAME:
+						DBLPClass.execute(inputCommand, this.userInput);
+						break;
+					case SEARCH_AUTHORS_PUBLICATIONS:
+						DBLPClass.execute(inputCommand, this.userInput);
+						break;
+					case SEARCH_PUBLICATION:
+						DBLPClass.execute(inputCommand, this.userInput);
+						break;
+					case EXIT:		                        
+			            return;       
+					default:
+						System.out.println("Error! You must insert a valid command...");
+						break;
+				}	
+		    } catch(DBLPClassException dblpce) {
+		    	throw new DBLPInterfaceException("display(): could not execute a DBLP operation...");
+		    }
+		}         
+	}		
+
+}
+
+

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPQueryCreator.java

@@ -1,0 +1,42 @@
+package inesc_id.gsd.bibtrek.app.dblp;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPSanitizer;
+
+public class DBLPQueryCreator {
+	
+	private final static String BASE_URL = "https://dblp.org/search";
+	
+	private final static String SEARCH_AUTHORS = "/author/api?q=";
+	private final static String SEARCH_PUBLICATIONS = "/publ/api?q=";
+	
+	private final static String FORMAT_JSON = "&format=json";
+	
+	public DBLPQueryCreator() {		
+	}
+	
+	public String searchAuthorByName(String authorName) {
+		String query;
+		DBLPSanitizer dblpSanitizer;
+		
+		dblpSanitizer = new DBLPSanitizer(authorName);
+		authorName = dblpSanitizer.sanitize();
+		
+		query = BASE_URL + SEARCH_AUTHORS + authorName + FORMAT_JSON;
+		
+		return query;
+	}
+	
+	public String searchForPublication(String publicationTitle) {
+		String query;
+		DBLPSanitizer dblpSanitizer;
+		
+		dblpSanitizer = new DBLPSanitizer(publicationTitle);
+		publicationTitle = dblpSanitizer.sanitize();
+		
+		query = BASE_URL + SEARCH_PUBLICATIONS + publicationTitle + FORMAT_JSON;
+		
+		return query;
+	}
+	
+	
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorSearchException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class AuthorSearchException extends SearchException {
+	
+	public AuthorSearchException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public AuthorSearchException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorsPublicationsSearchException.java

@@ -1,0 +1,12 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class AuthorsPublicationsSearchException extends SearchException {
+	
+	public AuthorsPublicationsSearchException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public AuthorsPublicationsSearchException(String errorMessage) {
+        super(errorMessage);
+    }
+}
+

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPClassException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class DBLPClassException extends SearchException {
+	
+	public DBLPClassException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public DBLPClassException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPConnectNeo4JException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class DBLPConnectNeo4JException extends Exception {
+	
+	public DBLPConnectNeo4JException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public DBLPConnectNeo4JException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPInterfaceException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class DBLPInterfaceException extends Exception {
+	
+	public DBLPInterfaceException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public DBLPInterfaceException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPNoSQLWriterException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class DBLPNoSQLWriterException extends Exception {
+	
+	public DBLPNoSQLWriterException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public DBLPNoSQLWriterException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPSanitizer.java

@@ -1,0 +1,45 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+import inesc_id.gsd.bibtrek.app.sanitizer.QuerySanitizer;
+
+public class DBLPSanitizer extends QuerySanitizer {
+	
+	private String name;
+		
+	public DBLPSanitizer(String name) {
+		this.name = name;
+	}
+	
+	@Override
+	public String sanitize() {
+		String sanitizedName;
+		StringBuilder stringBuilder = new StringBuilder();	
+		boolean first = true;	
+		boolean space = false;
+		char name_character;
+		
+		for(int i = 0; i<name.length(); i++) {
+			name_character = name.charAt(i);			
+			
+			if(name_character==' ') {	
+				space = true;								
+			} else if(!(name_character==' ') && (space==true && first == false)) {									
+				stringBuilder.append("+");
+				stringBuilder.append(name_character);				
+				space = false;
+			} else if(!(name_character==' ') && (space==false && first == false)) {
+				stringBuilder.append(name_character);
+				space = false;
+			} else if(!(name_character==' ') && (space==false && first == true)) {
+				stringBuilder.append(name_character);
+				first = false; 
+				space = false;				
+			}
+		}
+		
+		sanitizedName = stringBuilder.toString().toLowerCase();
+
+		return sanitizedName;
+	}	
+	
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/PublicationSearchException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class PublicationSearchException extends SearchException {
+	
+	public PublicationSearchException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public PublicationSearchException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/SearchBranchException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class SearchBranchException extends Exception {
+	
+	public SearchBranchException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public SearchBranchException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/SearchException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.dblp.exceptions;
+
+public class SearchException extends Exception {
+	
+	public SearchException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public SearchException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/AuthorJSONParser.java

@@ -1,0 +1,32 @@
+package inesc_id.gsd.bibtrek.app.dblp.parsing;
+
+import org.json.JSONObject;
+
+public class AuthorJSONParser extends JSONParser {
+	
+	private static final String AUTHOR = "author";
+	private static final String URL = "url";
+	
+	public AuthorJSONParser() {		
+	}
+
+	@Override
+	Object[] displayInfo(JSONObject info, int counter) {
+		Object[] tuple;
+		String author, url;
+		
+		author = (String) info.get(AUTHOR);
+		url = (String) info.get(URL);
+		
+		
+		System.out.println("(" + (counter+1) + ")");
+		System.out.print("- Author: ");
+		System.out.println(author);
+		System.out.print("- URL: ");
+		System.out.println(url);
+		
+		tuple = new Object[]{author, url};		
+		
+		return tuple;
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/JSONParser.java

@@ -1,0 +1,82 @@
+package inesc_id.gsd.bibtrek.app.dblp.parsing;
+
+import java.util.ArrayList;
+
+import org.json.JSONArray;
+import org.json.JSONObject;
+
+import inesc_id.gsd.bibtrek.app.utils.JSONUtils;
+
+public abstract class JSONParser {
+		
+	private static final String COMPLETIONS = "completions";
+	private static final String HIT = "hit";
+	private static final String HITS = "hits";
+	private static final String INFO = "info";
+	private static final String RESULT = "result";	
+	private static final String TOTAL = "@total";
+	
+	private String rawString;
+	
+	public JSONParser() {		
+	}
+	
+	public void setString(String rawString) {
+		this.rawString = rawString;
+	}
+	
+	private String getString() {
+		return this.rawString;
+	}
+	
+	public ArrayList<Object[]> parseString() {
+		int completion;
+		JSONObject result, hit, hits;
+		ArrayList<Object[]> tupleArrayList; 				
+		
+		result = new JSONObject(this.rawString);
+		hits = (JSONObject) result.get(RESULT);
+		
+		completion = checkCompletions(hits);
+		if(completion>0) {
+			hit = (JSONObject) hits.get(HITS);
+			tupleArrayList = displayHits(hit);
+		} else {
+			//TODO display message
+			tupleArrayList = new ArrayList();
+		}		
+		
+		return tupleArrayList;
+	}
+	
+	private ArrayList<Object[]> displayHits(JSONObject hit) {
+		Object[] tuple;
+		JSONArray hitArray;
+		JSONObject data, info;
+		ArrayList<Object[]> tupleArrayList; 
+		
+		tupleArrayList = new ArrayList();
+		tuple = new Object[0];
+		hitArray = (JSONArray) hit.get(HIT);
+		for(int i = 0; i<hitArray.length(); i++) {
+			data = (JSONObject) hitArray.get(i);
+			info = (JSONObject) data.get(INFO);
+			System.out.println("");
+			tuple = displayInfo(info, i);
+			tupleArrayList.add(tuple);
+		}		
+
+		return tupleArrayList;
+	}
+	
+	abstract Object[] displayInfo(JSONObject info, int counter);
+	
+	private int checkCompletions(JSONObject hits) {
+		int value;
+		JSONObject completions;
+				
+		completions = (JSONObject) hits.get(COMPLETIONS);
+		value = Integer.parseInt((String) completions.get(TOTAL));
+		return value;
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/PublicationJSONParser.java

@@ -1,0 +1,82 @@
+package inesc_id.gsd.bibtrek.app.dblp.parsing;
+
+import java.util.ArrayList;
+
+import org.json.JSONArray;
+import org.json.JSONObject;
+
+import inesc_id.gsd.bibtrek.app.utils.JSONUtils;
+
+public class PublicationJSONParser extends JSONParser {
+	
+	private static final String AUTHORS = "authors";
+	private static final String AUTHOR = "author";
+	private static final String DOI = "doi";
+	private static final String EE = "ee";
+	private static final String KEY = "key";
+	private static final String TITLE = "title";
+	private static final String TYPE = "type";
+	private static final String URL = "url";
+	private static final String VENUE = "venue";
+	private static final String YEAR = "year";
+	
+	public PublicationJSONParser() {
+		
+	}
+
+	@Override
+	Object[] displayInfo(JSONObject info, int counter) {
+		Object object;
+		Object[] tuple = null;
+		String author, title, venue, year, type, key, url;
+		ArrayList<Object> authorsArray;
+		
+		object = (Object) ((JSONObject) info.get(AUTHORS)).get(AUTHOR);
+		
+		key = (String) info.get(KEY);
+		title = (String) info.get(TITLE);
+		type = (String) info.get(TYPE);
+		url = (String) info.get(URL);
+		venue = (String) info.get(VENUE);
+		year = (String) info.get(YEAR);		
+		
+		System.out.println("(" + (counter+1) + ")");
+		System.out.print("- Title: ");
+		System.out.println(title);
+		System.out.print("- Authors: ");
+		System.out.println("");
+		
+		if(object instanceof JSONArray) {
+			authorsArray = JSONUtils.convertJSONArrayToArrayList((JSONArray) ((JSONObject) info.get(AUTHORS)).get(AUTHOR));
+			this.displayAuthorsList(authorsArray);
+			tuple = new Object[] {authorsArray, title, url, year, venue, type, key};
+		} else if(object instanceof String) {
+			author = (String) ((JSONObject) info.get(AUTHORS)).get(AUTHOR);
+			System.out.println("- Author: ");
+			System.out.println(author);
+			authorsArray = new ArrayList<Object>();
+			authorsArray.add(author);
+			tuple = new Object[] {authorsArray, title, url, year, venue, type, key};
+		}
+		
+		System.out.print("- Venue: ");
+		System.out.println(venue);
+		System.out.print("- Year: ");
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorSearch.java

@@ -1,0 +1,59 @@
+package inesc_id.gsd.bibtrek.app.dblp.search;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
+import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
+import inesc_id.gsd.bibtrek.app.dblp.writer.AuthorDBLPNoSQLWriter;
+
+public class AuthorSearch extends Search {
+	
+	private String choice;
+	private DBLPQueryCreator queryCreator; 
+	private Scanner userInput;
+	
+	public AuthorSearch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {
+		this.queryCreator = queryCreator;
+		this.userInput = userInput;
+		this.choice = choice;
+	}
+
+	@Override
+	public ArrayList<Object[]> search() throws AuthorSearchException {
+		String query, authorName, getRequest;		
+		AuthorJSONParser authorJSONParser;	
+		ArrayList<Object[]> tupleArrayList;
+		SearchBranch searchBranch;
+		ArrayList<Object[]> authorsList = null;
+				
+		authorJSONParser = new AuthorJSONParser();
+		searchBranch = new SearchBranch(this.choice, this.userInput);
+		System.out.print("Type the author's name: ");	            									
+		authorName = this.userInput.nextLine(); 
+		query = this.queryCreator.searchAuthorByName(authorName);		
+		try {
+			getRequest = this.executeQuery(query);
+		} catch (SearchException se) {
+			throw new AuthorSearchException("search(): could not execute the query: \"" + query + "\".");
+		}
+		authorJSONParser.setString(getRequest);
+		System.out.println("");
+		System.out.println("(*) Authors Found: ");
+		tupleArrayList = authorJSONParser.parseString();
+		if(!tupleArrayList.isEmpty()) {		
+			try {
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorsPublicationsSearch.java

@@ -1,0 +1,40 @@
+package inesc_id.gsd.bibtrek.app.dblp.search;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
+import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.AuthorsPublicationsSearchBranch;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
+
+public class AuthorsPublicationsSearch {;
+	
+	private String choice;
+	private DBLPQueryCreator queryCreator; 
+	private Scanner userInput;	
+	
+	
+	public AuthorsPublicationsSearch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {
+		this.queryCreator = queryCreator;
+		this.userInput = userInput;
+		this.choice = choice;
+	}
+
+	public void search(ArrayList<Object[]> tupleArrayList) throws AuthorsPublicationsSearchException {		
+		AuthorsPublicationsSearchBranch authorsPublicationsSearchBranch;										
+
+		if(!tupleArrayList.isEmpty()) {			
+			try {											
+				authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.queryCreator, this.userInput, this.choice);
+				authorsPublicationsSearchBranch.choose(tupleArrayList);
+			} catch (PublicationSearchException pse) {
+				throw new AuthorsPublicationsSearchException("search(): could not search for publication.");
+			}			
+		}		
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/PublicationSearch.java

@@ -1,0 +1,90 @@
+package inesc_id.gsd.bibtrek.app.dblp.search;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
+import inesc_id.gsd.bibtrek.app.dblp.parsing.PublicationJSONParser;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
+
+public class PublicationSearch extends Search {
+	
+	private String choice;
+	private DBLPQueryCreator queryCreator; 
+	private Scanner userInput;	
+	
+	public PublicationSearch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {		
+		this.queryCreator = queryCreator;
+		this.userInput = userInput;
+		this.choice = choice;
+	}
+
+	@Override
+	public ArrayList<Object[]> search() throws PublicationSearchException {
+		String query, userChoice, getRequest;		
+		PublicationJSONParser publicationJSONParser;	
+		ArrayList<Object[]> tupleArrayList = null;
+		SearchBranch searchBranch;
+				
+		publicationJSONParser = new PublicationJSONParser();
+		searchBranch = new SearchBranch(this.choice, this.userInput);
+		
+		System.out.print("Type the publication's title: ");
+				
+		userChoice = this.userInput.nextLine(); 
+				
+		query = queryCreator.searchForPublication(userChoice);		
+		
+		try {
+			getRequest = this.executeQuery(query);
+		} catch (SearchException se) {
+			throw new PublicationSearchException("search(): could not execute the query: \"" + query + "\".");
+		}
+		publicationJSONParser.setString(getRequest);
+		System.out.println("");
+		System.out.println("(*) Publications Found: ");
+		tupleArrayList = publicationJSONParser.parseString();
+		if(!tupleArrayList.isEmpty()) {					
+			try {
+				searchBranch.choose(tupleArrayList);
+			} catch (SearchBranchException sbe) {
+				throw new PublicationSearchException("search(): could not search for publication.");
+			}			
+		}
+		
+		return tupleArrayList;
+	}
+	
+	public void search(String title) throws PublicationSearchException {
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/Search.java

@@ -1,0 +1,30 @@
+package inesc_id.gsd.bibtrek.app.dblp.search;
+
+import java.util.ArrayList;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
+import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
+import inesc_id.gsd.bibtrek.app.http.HTTPClient;
+
+public abstract class Search {
+	
+	public Search() {
+	}
+	
+	public String executeQuery(String query) throws SearchException {
+		HTTPClient httpClient = new HTTPClient();
+		String getRequest;
+		try {
+			getRequest = httpClient.getRequest(query);
+			return getRequest;
+		} catch(HTTPClientException httpce) {
+			throw new SearchException("executeQuery(): could not execute a get request for"
+					+ " the website with url: \"" + query + "\".");
+		}
+	}
+		
+	public abstract ArrayList<Object[]> search() throws Exception;
+
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/AuthorsPublicationsSearchBranch.java

@@ -1,0 +1,57 @@
+package inesc_id.gsd.bibtrek.app.dblp.search.condition;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
+import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
+
+public class AuthorsPublicationsSearchBranch {
+	
+	private String choice;
+	private DBLPQueryCreator queryCreator;
+	private Scanner userInput;
+	
+	public AuthorsPublicationsSearchBranch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {
+		this.choice = choice;
+		this.queryCreator = queryCreator;
+		this.userInput = userInput;
+	}
+	
+	public void choose(ArrayList<Object[]> tupleArrayList) throws PublicationSearchException {
+		String authorName, continueChoice;
+		PublicationSearch publicationSearch;
+		
+		publicationSearch = new PublicationSearch(this.queryCreator, this.userInput, this.choice);
+		
+		for(int i = 0; i<tupleArrayList.size(); i++) {
+			authorName = (String) tupleArrayList.get(i)[0];
+			if(i>=1) {
+				while(true) {
+					boolean breakCycle = false;
+					System.out.println("");
+					System.out.print("(*) Do you want to fetch the publications of the other authors you have fetched? Type [Y|N]: ");											
+					continueChoice = this.userInput.nextLine();
+					switch(continueChoice) {
+						case "Y":
+							publicationSearch.search(authorName);
+							breakCycle = true;
+							break;
+						case "N":									
+							return;
+						default:
+							System.out.println("You must insert a valid choice...");
+					}
+					if(breakCycle)
+						break;
+				}
+			} else {
+				publicationSearch.search(authorName);
+			}
+		}
+	}
+	
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/SearchBranch.java

@@ -1,0 +1,112 @@
+package inesc_id.gsd.bibtrek.app.dblp.search.condition;
+
+import java.util.ArrayList;
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
+
+public class SearchBranch {
+	
+	private final static String AUTHOR = "author";
+	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
+	private final static String PUBLICATION = "publication";
+	
+	private String choice;
+	private Scanner userInput;
+	
+	public SearchBranch(String choice, Scanner userInput) {
+		this.choice = choice;
+		this.userInput = userInput;
+	}
+	
+	@SuppressWarnings("unchecked")
+	public ArrayList<Object[]> choose(ArrayList<Object[]> tupleArrayList) throws SearchBranchException {
+		Object[] tuple;
+		String publicationChoice;
+		boolean exit = false;
+		
+		ArrayList<Object[]> addedPublications = new ArrayList<Object[]>();
+		while(true) {
+						
+			if(this.choice.equals(AUTHOR)) {
+				System.out.println("");			
+				System.out.println("(*) Author's Menu");
+			} else if(this.choice.equals(AUTHORS_PUBLICATIONS)) {
+				System.out.println("");
+				System.out.println("(*) Author's Publication Menu");
+			} else if(this.choice.equals(PUBLICATION)) {
+				System.out.println("");
+				System.out.println("(*) Publications Menu");
+			}
+			System.out.println("");
+			System.out.println("(a)");
+			System.out.println("- Add all of the available choices and exits the menu ; ");
+			System.out.println("");
+			System.out.println("(es)");
+			System.out.println("- Exits the choice menu and saves the configuration you have chosen ;");
+			System.out.println("");
+			System.out.println("(e!)");
+			System.out.println("- Exits the choice menu without saving ;");
+			System.out.println(""); 
+			System.out.print("Pick one of the publications to insert in the database: ");	            									
+			publicationChoice = this.userInput.nextLine();
+
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/WriteConditionFactory.java

@@ -1,0 +1,28 @@
+package inesc_id.gsd.bibtrek.app.dblp.search.condition;
+
+import java.util.ArrayList;
+
+import inesc_id.gsd.bibtrek.app.dblp.writer.AuthorDBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
+import inesc_id.gsd.bibtrek.app.dblp.writer.PublicationsDBLPNoSQLWriter;
+
+public class WriteConditionFactory {
+	
+	private final static String AUTHOR = "author";
+	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
+	private final static String PUBLICATION = "publication";
+	
+	public static DBLPNoSQLWriter getWriter(ArrayList<Object[]> tupleArrayList, String condition) {
+		DBLPNoSQLWriter writer = null; 		
+		switch(condition) {
+			case AUTHOR:
+				writer = new AuthorDBLPNoSQLWriter(tupleArrayList);
+				break;
+			case AUTHORS_PUBLICATIONS:
+			case PUBLICATION:
+				writer = new PublicationsDBLPNoSQLWriter(tupleArrayList);
+				break;					
+		}
+		return writer;	
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/AuthorDBLPNoSQLWriter.java

@@ -1,0 +1,46 @@
+package inesc_id.gsd.bibtrek.app.dblp.writer;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Iterator;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
+
+public class AuthorDBLPNoSQLWriter extends DBLPNoSQLWriter{
+	
+	public AuthorDBLPNoSQLWriter(ArrayList<Object[]> listToWrite) {
+		super(listToWrite);
+	}
+	
+	public synchronized void writeToFile() throws DBLPNoSQLWriterException {		
+		BufferedWriter bufferedWriter;
+		Iterator<Object[]> iter;
+		Object[] tuple;
+		String author, url;
+		
+		iter = listToWrite.iterator();
+		
+		try {
+			bufferedWriter = new BufferedWriter(new FileWriter(getCurrentFile(), true));
+			
+			while(iter.hasNext()) {
+				tuple = iter.next();
+				author = (String) tuple[0];
+				url = (String) tuple[1];
+				bufferedWriter.append(TimeUtils.getCurrentTimeString() + ": ");
+				bufferedWriter.append("CREATE (" 
+						+ author.replaceAll(REPLACE_REGEX, "") + ":Author {name:\"" 
+						+ author + "\", url:\"" + url + "\"})");
+				
+				bufferedWriter.append("\n");												
+			}			
+			bufferedWriter.close();
+		} catch (IOException ioe) {
+			throw new DBLPNoSQLWriterException("writeToFile(): could not write to the current state.");
+		}
+		
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/DBLPNoSQLWriter.java

@@ -1,0 +1,29 @@
+package inesc_id.gsd.bibtrek.app.dblp.writer;
+
+import java.util.ArrayList;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
+
+public abstract class DBLPNoSQLWriter {
+	
+	final static String REPLACE_REGEX = "[\\W\\s]";
+	
+	private final static String DBLP_NOSQL_PATH = "src/main/java/inesc_id/gsd/bibtrek/app/nosql/dblp/";
+
+	ArrayList<Object[]> listToWrite;
+	
+	public DBLPNoSQLWriter(ArrayList<Object[]> listToWrite) {
+		this.listToWrite = listToWrite;
+	}
+	
+	public abstract void writeToFile() throws DBLPNoSQLWriterException;
+	
+	protected String getCurrentFile() {
+		String fileName;
+		
+		fileName = DBLP_NOSQL_PATH + TimeUtils.getCurrentTimeString() + ".nosql";
+		
+		return fileName;
+	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/PublicationsDBLPNoSQLWriter.java

@@ -1,0 +1,72 @@
+package inesc_id.gsd.bibtrek.app.dblp.writer;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Iterator;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
+import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
+
+public class PublicationsDBLPNoSQLWriter extends DBLPNoSQLWriter{
+	
+	public PublicationsDBLPNoSQLWriter(ArrayList<Object[]> listToWrite) {
+		super(listToWrite);
+	}
+	
+	@SuppressWarnings("unchecked")
+	public synchronized void writeToFile() throws DBLPNoSQLWriterException {
+		BufferedWriter bufferedWriter;
+		Iterator<Object[]> iter;
+		Object[] tuple;
+		ArrayList<String> authorsArrayList;
+		String author = "no_author", title, url, year, venue, type, key;
+		
+		iter = listToWrite.iterator();
+		authorsArrayList = new ArrayList<String>();
+		
+		try {
+			bufferedWriter = new BufferedWriter(new FileWriter(getCurrentFile(), true));
+			
+			while(iter.hasNext()) {
+				tuple = iter.next();
+				
+				bufferedWriter.append(TimeUtils.getCurrentTimeString() + ": ");				
+				
+				title = (String) tuple[1];
+				url = (String) tuple[2];
+				year = (String) tuple[3];
+				venue = (String) tuple[4];
+				type = (String) tuple[5];
+				key = (String) tuple[6];				
+				
+				bufferedWriter.append("CREATE (" + title.replaceAll(REPLACE_REGEX, "")
+						+ ":Publication {title:\"" + title 
+						+ "\", url:\"" + url + "\", year:\"" + (int) Integer.valueOf(year) 
+						+ "\", venue:\"" + venue + "\", type:\"" + type 
+						+ "\", key:\"" + key + "\"})");				
+				authorsArrayList = (ArrayList<String>) tuple[0];
+				for(String authorIter : authorsArrayList) {
+					author = authorIter;					
+					
+					bufferedWriter.append(" ");
+					
+					bufferedWriter.append("CREATE (" 
+							+ author.replaceAll("\\W", "") + ":Author {name:\"" + author + "\"})");
+					
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/exceptions/HTTPClientException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.exceptions;
+
+public class HTTPClientException extends Exception {
+	
+	public HTTPClientException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public HTTPClientException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/exceptions/MainInterfaceException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.exceptions;
+
+public class MainInterfaceException extends Exception {
+	
+	public MainInterfaceException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public MainInterfaceException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/exceptions/WriteNeo4JThreadException.java

@@ -1,0 +1,11 @@
+package inesc_id.gsd.bibtrek.app.exceptions;
+
+public class WriteNeo4JThreadException extends Exception {
+	
+	public WriteNeo4JThreadException(String errorMessage, Throwable err) {
+        super(errorMessage, err);
+    }
+    public WriteNeo4JThreadException(String errorMessage) {
+        super(errorMessage);
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/http/HTTPClient.java

@@ -1,0 +1,60 @@
+package inesc_id.gsd.bibtrek.app.http;
+
+import java.io.BufferedReader;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.net.HttpURLConnection;
+import java.net.MalformedURLException;
+import java.net.URL;
+
+import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
+
+public class HTTPClient {
+	
+	private final static String USER_AGENT = "Mozilla/5.0";
+	
+	public HTTPClient() {		
+	}
+	
+    // HTTP GET request
+ 	public String getRequest(String query) throws HTTPClientException { 		
+ 		
+ 		URL url;
+ 		
+		try {
+			url = new URL(query);
+			
+			HttpURLConnection con = (HttpURLConnection) url.openConnection();
+
+	 		// optional default is GET
+	 		con.setRequestMethod("GET");
+
+	 		//add request header
+	 		con.setRequestProperty("User-Agent", USER_AGENT);
+
+	 		int responseCode = con.getResponseCode();
+
+	 		BufferedReader in = new BufferedReader(new InputStreamReader(con.getInputStream()));
+	 		
+	 		String inputLine;
+	 		StringBuffer response = new StringBuffer();
+
+	 		while ((inputLine = in.readLine()) != null) {
+	 			response.append(inputLine);
+	 		}
+	 		
+	 		in.close();
+
+	 		//print result
+	 		return response.toString();
+	 		
+		} catch (MalformedURLException murle) {
+			throw new HTTPClientException("getRequest(): the url: \"" 
+					+ query + "\" is not properly structured.");
+		} catch (IOException ioe) {
+			throw new HTTPClientException("getRequest(): could not open a connection"
+					+ " for the website with url: \"" + query + "\".");
+		}
+
+ 	}
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/main/MainClass.java

@@ -1,0 +1,26 @@
+package inesc_id.gsd.bibtrek.app.main;
+
+import java.io.OutputStream;
+import java.io.PrintStream;
+
+import inesc_id.gsd.bibtrek.app.exceptions.MainClassException;
+import inesc_id.gsd.bibtrek.app.exceptions.MainInterfaceException;
+import inesc_id.gsd.bibtrek.app.neo4j.WriteNeo4JThread;
+
+public class MainClass {		
+	
+    public static void main(String[] args ) throws MainClassException {
+    	WriteNeo4JThread neo4JThread;
+		
+    	MainInterface mainInterface = MainInterface.getInstance();    	
+    	try {
+    		neo4JThread = new WriteNeo4JThread();
+    		//new Thread(neo4JThread).start();
+			mainInterface.display();
+		} catch (MainInterfaceException mie) {
+			throw new MainClassException("main(): an error occurred while displaying the menu! Aborting...");
+		}
+    }
+    
+
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/main/MainInterface.java

@@ -1,0 +1,71 @@
+package inesc_id.gsd.bibtrek.app.main;
+
+import java.util.Scanner;
+
+import inesc_id.gsd.bibtrek.app.dblp.DBLPInterface;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
+import inesc_id.gsd.bibtrek.app.exceptions.MainInterfaceException;
+
+public class MainInterface {
+ 
+    private static MainInterface main_interface = null; 
+    
+    private final static String DBLP = "dblp";    
+    private final static String EXIT = "exit";
+   
+    private MainInterface() {  
+    } 
+  
+    public static MainInterface getInstance() { 
+        if (main_interface == null) 
+        	main_interface = new MainInterface(); 
+  
+        return main_interface; 
+    } 
+    
+    public void displayDBLP(Scanner userInput) throws MainInterfaceException {
+    	DBLPInterface dblpInterface;
+    	
+    	dblpInterface = new DBLPInterface(userInput);
+		
+    	try {
+    		dblpInterface.display();
+    	} catch(DBLPInterfaceException dblpie) {
+    		throw new MainInterfaceException("displayDBLP(): could not display the DBLP query menu...");
+    	}
+    	
+    }
+    
+    public void display() throws MainInterfaceException {    	
+    	String chosenLibrary;
+    	    	
+    	System.out.println("BIBTREK");
+    	System.out.println("");
+    	
+    	Scanner userInput = new Scanner(System.in); 
+    	
+    	while(true) {        	            
+            System.out.println("Pick one of the options in the menu.");     
+            System.out.println("");
+            System.out.println("(dblp) Digital Bibliography & Library Project");
+            System.out.println("");
+            System.out.println("(exit) Exits the program");
+            System.out.println("");
+            System.out.print("Type one of the above commands: ");            
+            chosenLibrary = userInput.nextLine();                                                 
+            System.out.println("");  
+            
+             
+            switch(chosenLibrary) {            
+            	case DBLP:    
+            		this.displayDBLP(userInput);            		
+            		break;
+            	case EXIT:
+            		return;
+            	default:
+            		System.out.println("Error! You must insert a valid command...");
+            		break;
+            }                       
+        }
+    }
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/neo4j/ConnectNeo4J.java

@@ -1,0 +1,74 @@
+package inesc_id.gsd.bibtrek.app.neo4j;
+
+import org.neo4j.driver.v1.AuthTokens;
+import org.neo4j.driver.v1.Driver;
+import org.neo4j.driver.v1.GraphDatabase;
+import org.neo4j.driver.v1.Session;
+import org.neo4j.driver.v1.StatementResult;
+import org.neo4j.driver.v1.Transaction;
+import org.neo4j.driver.v1.TransactionWork;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
+
+import static org.neo4j.driver.v1.Values.parameters;
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.IOException;
+import java.io.OutputStream;
+import java.io.PrintStream;
+
+public class ConnectNeo4J implements AutoCloseable {
+	
+    private final Driver driver;
+    
+    public ConnectNeo4J(String uri, String user, String password) {
+        driver = GraphDatabase.driver(uri, AuthTokens.basic(user, password));
+    }
+
+    @Override
+    public void close() {
+        driver.close();
+    }
+
+    private void store(final String query) {
+    	Session session = driver.session();
+	
+        Boolean r = session.writeTransaction(new TransactionWork<Boolean>() {
+            @Override
+            public Boolean execute(Transaction tx) {     
+            	System.out.println(query);
+                StatementResult result = tx.run(query, parameters());
+                return true;
+            }
+        });
+    }
+    
+    private synchronized boolean read(String fileName) throws DBLPConnectNeo4JException {
+    	BufferedReader bufferedReader;
+    	String line, query, queryTuple[];
+    	try {
+			bufferedReader = new BufferedReader(new FileReader(fileName));
+			
+			while((line = bufferedReader.readLine()) != null) {
+				if(!line.equals("") ) {
+					queryTuple = line.split(": ", 2);
+					query = queryTuple[1];	
+					this.store(query);
+				}
+			}
+			
+			return true;
+			
+		} catch (FileNotFoundException fnfe) {
+			throw new DBLPConnectNeo4JException("read(): could not open file: \"" + fileName + "\".");
+		} catch (IOException ioe) {
+			throw new DBLPConnectNeo4JException("read(): could not read the file: \"" + fileName + "\".");
+		}    	
+    }
+    
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/neo4j/WriteNeo4JThread.java

@@ -1,0 +1,100 @@
+package inesc_id.gsd.bibtrek.app.neo4j;
+
+import java.io.File;
+import java.util.ArrayList;
+
+import org.neo4j.driver.v1.exceptions.ServiceUnavailableException;
+
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
+import inesc_id.gsd.bibtrek.app.exceptions.WriteNeo4JThreadException;
+import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
+
+public class WriteNeo4JThread implements Runnable {
+	
+	private final static String GET_FILE = "\\/.\\d*_\\d*.nosql";
+	
+	private final static String GRAPH_PASSWORD = "graph";
+	
+	private final static String NOSQL_PATH = "src/main/java/inesc_id/gsd/bibtrek/app/nosql/";
+	
+	private final static String PROCESSED = "processed";
+	private final static String PROCESSED_REGEX = ".*\\/processed";
+	
+	@Override
+	public void run() {				
+		try {
+			while(true) {
+				Thread.sleep(5*1000);
+				this.execute();
+			}
+		} catch (InterruptedException ie) {
+			System.out.println("run(): the writing thread was interrupted!");
+		} catch (WriteNeo4JThreadException wneo4jte) {
+			System.out.println(wneo4jte.getMessage());
+		}
+	}
+	
+	private void execute() throws WriteNeo4JThreadException {
+		File noSQLPath;
+		File[] listOfFiles;
+		ArrayList<String> fileNameArrayList = new ArrayList<String>();
+		
+		noSQLPath = new File(NOSQL_PATH);
+		listOfFiles = noSQLPath.listFiles();
+		
+		fileNameArrayList = this.recursiveDirectoryList(noSQLPath, listOfFiles, fileNameArrayList);
+		this.write(fileNameArrayList);				
+	}
+	
+	private ArrayList<String> recursiveDirectoryList(File path, File[] listOfFiles, ArrayList<String> fileNameArrayList) {
+		String fileName;
+		File newPath;
+		File[] newListOfFiles;
+		
+		for (int i = 0; i < listOfFiles.length; i++) {			
+			if (listOfFiles[i].isFile()) {
+				fileName = path + File.separator + listOfFiles[i].getName();
+				fileNameArrayList.add(fileName);				
+			} else if (listOfFiles[i].isDirectory() && !listOfFiles[i].toString().matches(PROCESSED_REGEX)) {				
[…]

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/utils/JSONUtils.java

@@ -1,0 +1,20 @@
+package inesc_id.gsd.bibtrek.app.utils;
+
+import java.util.ArrayList;
+import org.json.JSONArray;
+
+public class JSONUtils {
+	
+	public static ArrayList<Object> convertJSONArrayToArrayList(JSONArray jasonArray) {
+		ArrayList<Object> arrayList = new ArrayList<Object>();     
+		 
+		if (jasonArray != null) { 
+			for (int i=0; i<jasonArray.length(); i++) { 
+				arrayList.add(jasonArray.get(i));
+			} 
+		}
+		
+		return arrayList;
+	}
+	
+}

### 2019-07-30 app/src/main/java/inesc_id/gsd/bibtrek/app/utils/TimeUtils.java

@@ -1,0 +1,23 @@
+package inesc_id.gsd.bibtrek.app.utils;
+
+import java.text.SimpleDateFormat;
+import java.util.Date;
+
+public class TimeUtils {
+	
+	private TimeUtils() {
+		
+	}
+	
+	public static String getCurrentTimeString() {
+		String dateString;
+		Date date;
+		SimpleDateFormat format;
+		
+		date = new Date();
+		format = new SimpleDateFormat("ddMMyyyy_HHmmssSSSSSS");	
+		dateString = format.format(date);
+		
+		return dateString;
+	}
+}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPClass.java
bug fixing

@@ -1,73 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp;
-
-import java.util.ArrayList;
-import java.util.Scanner;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.search.AuthorSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.AuthorsPublicationsSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.PublicationSearch;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
-import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-
-public class DBLPClass {
-	
-	private final static String AUTHOR = "author";
-	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
-	private final static String PUBLICATION = "publication";
-	
-	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
-	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
-	private static final String SEARCH_PUBLICATION = "p";
-	
-	
-	public static void execute(String inputCommand, Scanner userInput) throws DBLPClassException {
-		DBLPQueryCreator queryCreator;		
-		String query, authorName, publicationTitle, getRequest;		
-		AuthorSearch authorSearch;
-		AuthorsPublicationsSearch authorsPublicationsSearch;
-		PublicationSearch publicationSearch;
-		DBLPNoSQLWriter dblpNoSQLWriter;
-		ArrayList<Object[]> tupleArrayList; 
-				
-		queryCreator = new DBLPQueryCreator();                        		 
-		
-		try {
-			switch(inputCommand) {
-				case SEARCH_AUTHOR_BY_NAME:
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPInterface.java

@@ -1,64 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp;
-
-import java.util.Scanner;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPClassException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPInterfaceException;
-
-public class DBLPInterface {
-		
-	private static final String SEARCH_AUTHOR_BY_NAME = "a"; 
-	private static final String SEARCH_AUTHORS_PUBLICATIONS = "ap";
-	private static final String SEARCH_PUBLICATION = "p";
-	private final static String EXIT = "e";	
-	
-	private Scanner userInput;
-	
-	public DBLPInterface(Scanner userInput) {
-		this.userInput = userInput; 		
-	}
-		
-	public void display() throws DBLPInterfaceException {
-		String inputCommand;
-		          
-		while(true) {
-			System.out.println("");
-			System.out.println("(*)  : DBLP MENU");
-			System.out.println("");
-		    System.out.println("(a)  : Searches for an author by name ;");
-		    System.out.println("(ap) : Searches for an author's publications by name ;");
-		    System.out.println("(p)  : Searches for a publications by title ;");
-		    System.out.println("(e)  : Exits the DBLP query menu ;");
-		    System.out.println("");
-		    System.out.print("Type one of the above commands: ");
-		    
-		    inputCommand = this.userInput.nextLine();
-		    
-		    System.out.println("");
-		    
-		    try {
-				switch(inputCommand) {
-					case SEARCH_AUTHOR_BY_NAME:
-						DBLPClass.execute(inputCommand, this.userInput);
-						break;
-					case SEARCH_AUTHORS_PUBLICATIONS:
-						DBLPClass.execute(inputCommand, this.userInput);
-						break;
-					case SEARCH_PUBLICATION:
-						DBLPClass.execute(inputCommand, this.userInput);
-						break;
-					case EXIT:		                        
-			            return;       
-					default:
-						System.out.println("Error! You must insert a valid command...");
-						break;
-				}	
-		    } catch(DBLPClassException dblpce) {
-		    	throw new DBLPInterfaceException("display(): could not execute a DBLP operation...");
-		    }
-		}         
-	}		
-
-}
-
-

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/DBLPQueryCreator.java

@@ -1,42 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPSanitizer;
-
-public class DBLPQueryCreator {
-	
-	private final static String BASE_URL = "https://dblp.org/search";
-	
-	private final static String SEARCH_AUTHORS = "/author/api?q=";
-	private final static String SEARCH_PUBLICATIONS = "/publ/api?q=";
-	
-	private final static String FORMAT_JSON = "&format=json";
-	
-	public DBLPQueryCreator() {		
-	}
-	
-	public String searchAuthorByName(String authorName) {
-		String query;
-		DBLPSanitizer dblpSanitizer;
-		
-		dblpSanitizer = new DBLPSanitizer(authorName);
-		authorName = dblpSanitizer.sanitize();
-		
-		query = BASE_URL + SEARCH_AUTHORS + authorName + FORMAT_JSON;
-		
-		return query;
-	}
-	
-	public String searchForPublication(String publicationTitle) {
-		String query;
-		DBLPSanitizer dblpSanitizer;
-		
-		dblpSanitizer = new DBLPSanitizer(publicationTitle);
-		publicationTitle = dblpSanitizer.sanitize();
-		
-		query = BASE_URL + SEARCH_PUBLICATIONS + publicationTitle + FORMAT_JSON;
-		
-		return query;
-	}
-	
-	
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorSearchException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class AuthorSearchException extends SearchException {
-	
-	public AuthorSearchException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public AuthorSearchException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/AuthorsPublicationsSearchException.java

@@ -1,12 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class AuthorsPublicationsSearchException extends SearchException {
-	
-	public AuthorsPublicationsSearchException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public AuthorsPublicationsSearchException(String errorMessage) {
-        super(errorMessage);
-    }
-}
-

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPClassException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class DBLPClassException extends SearchException {
-	
-	public DBLPClassException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public DBLPClassException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPInterfaceException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class DBLPInterfaceException extends Exception {
-	
-	public DBLPInterfaceException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public DBLPInterfaceException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPNoSQLWriterException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class DBLPNoSQLWriterException extends Exception {
-	
-	public DBLPNoSQLWriterException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public DBLPNoSQLWriterException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/DBLPSanitizer.java

@@ -1,45 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-import inesc_id.gsd.bibtrek.app.sanitizer.QuerySanitizer;
-
-public class DBLPSanitizer extends QuerySanitizer {
-	
-	private String name;
-		
-	public DBLPSanitizer(String name) {
-		this.name = name;
-	}
-	
-	@Override
-	public String sanitize() {
-		String sanitizedName;
-		StringBuilder stringBuilder = new StringBuilder();	
-		boolean first = true;	
-		boolean space = false;
-		char name_character;
-		
-		for(int i = 0; i<name.length(); i++) {
-			name_character = name.charAt(i);			
-			
-			if(name_character==' ') {	
-				space = true;								
-			} else if(!(name_character==' ') && (space==true && first == false)) {									
-				stringBuilder.append("+");
-				stringBuilder.append(name_character);				
-				space = false;
-			} else if(!(name_character==' ') && (space==false && first == false)) {
-				stringBuilder.append(name_character);
-				space = false;
-			} else if(!(name_character==' ') && (space==false && first == true)) {
-				stringBuilder.append(name_character);
-				first = false; 
-				space = false;				
-			}
-		}
-		
-		sanitizedName = stringBuilder.toString().toLowerCase();
-
-		return sanitizedName;
-	}	
-	
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/PublicationSearchException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class PublicationSearchException extends SearchException {
-	
-	public PublicationSearchException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public PublicationSearchException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/exceptions/SearchException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.exceptions;
-
-public class SearchException extends Exception {
-	
-	public SearchException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public SearchException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/AuthorJSONParser.java

@@ -1,32 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.parsing;
-
-import org.json.JSONObject;
-
-public class AuthorJSONParser extends JSONParser {
-	
-	private static final String AUTHOR = "author";
-	private static final String URL = "url";
-	
-	public AuthorJSONParser() {		
-	}
-
-	@Override
-	Object[] displayInfo(JSONObject info, int counter) {
-		Object[] tuple;
-		String author, url;
-		
-		author = (String) info.get(AUTHOR);
-		url = (String) info.get(URL);
-		
-		
-		System.out.println("(" + (counter+1) + ")");
-		System.out.print("- Author: ");
-		System.out.println(author);
-		System.out.print("- URL: ");
-		System.out.println(url);
-		
-		tuple = new Object[]{author, url};		
-		
-		return tuple;
-	}
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/JSONParser.java

@@ -1,82 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.parsing;
-
-import java.util.ArrayList;
-
-import org.json.JSONArray;
-import org.json.JSONObject;
-
-import inesc_id.gsd.bibtrek.app.utils.JSONUtils;
-
-public abstract class JSONParser {
-		
-	private static final String COMPLETIONS = "completions";
-	private static final String HIT = "hit";
-	private static final String HITS = "hits";
-	private static final String INFO = "info";
-	private static final String RESULT = "result";	
-	private static final String TOTAL = "@total";
-	
-	private String rawString;
-	
-	public JSONParser() {		
-	}
-	
-	public void setString(String rawString) {
-		this.rawString = rawString;
-	}
-	
-	private String getString() {
-		return this.rawString;
-	}
-	
-	public ArrayList<Object[]> parseString() {
-		int completion;
-		JSONObject result, hit, hits;
-		ArrayList<Object[]> tupleArrayList; 				
-		
-		result = new JSONObject(this.rawString);
-		hits = (JSONObject) result.get(RESULT);
-		
-		completion = checkCompletions(hits);
-		if(completion>0) {
-			hit = (JSONObject) hits.get(HITS);
-			tupleArrayList = displayHits(hit);
-		} else {
-			//TODO display message
-			tupleArrayList = new ArrayList();
-		}		
-		
-		return tupleArrayList;
-	}
-	
-	private ArrayList<Object[]> displayHits(JSONObject hit) {
-		Object[] tuple;
-		JSONArray hitArray;
-		JSONObject data, info;
-		ArrayList<Object[]> tupleArrayList; 
-		
-		tupleArrayList = new ArrayList();
-		tuple = new Object[0];
-		hitArray = (JSONArray) hit.get(HIT);
-		for(int i = 0; i<hitArray.length(); i++) {
-			data = (JSONObject) hitArray.get(i);
-			info = (JSONObject) data.get(INFO);
-			System.out.println("");
-			tuple = displayInfo(info, i);
-			tupleArrayList.add(tuple);
-		}		
-
-		return tupleArrayList;
-	}
-	
-	abstract Object[] displayInfo(JSONObject info, int counter);
-	
-	private int checkCompletions(JSONObject hits) {
-		int value;
-		JSONObject completions;
-				
-		completions = (JSONObject) hits.get(COMPLETIONS);
-		value = Integer.parseInt((String) completions.get(TOTAL));
-		return value;
-	}
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/parsing/PublicationJSONParser.java

@@ -1,82 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.parsing;
-
-import java.util.ArrayList;
-
-import org.json.JSONArray;
-import org.json.JSONObject;
-
-import inesc_id.gsd.bibtrek.app.utils.JSONUtils;
-
-public class PublicationJSONParser extends JSONParser {
-	
-	private static final String AUTHORS = "authors";
-	private static final String AUTHOR = "author";
-	private static final String DOI = "doi";
-	private static final String EE = "ee";
-	private static final String KEY = "key";
-	private static final String TITLE = "title";
-	private static final String TYPE = "type";
-	private static final String URL = "url";
-	private static final String VENUE = "venue";
-	private static final String YEAR = "year";
-	
-	public PublicationJSONParser() {
-		
-	}
-
-	@Override
-	Object[] displayInfo(JSONObject info, int counter) {
-		Object object;
-		Object[] tuple = null;
-		String author, title, venue, year, type, key, url;
-		ArrayList<Object> authorsArray;
-		
-		object = (Object) ((JSONObject) info.get(AUTHORS)).get(AUTHOR);
-		
-		key = (String) info.get(KEY);
-		title = (String) info.get(TITLE);
-		type = (String) info.get(TYPE);
-		url = (String) info.get(URL);
-		venue = (String) info.get(VENUE);
-		year = (String) info.get(YEAR);		
-		
-		System.out.println("(" + (counter+1) + ")");
-		System.out.print("- Title: ");
-		System.out.println(title);
-		System.out.print("- Authors: ");
-		System.out.println("");
-		
-		if(object instanceof JSONArray) {
-			authorsArray = JSONUtils.convertJSONArrayToArrayList((JSONArray) ((JSONObject) info.get(AUTHORS)).get(AUTHOR));
-			this.displayAuthorsList(authorsArray);
-			tuple = new Object[] {authorsArray, title, url, year, venue, type, key};
-		} else if(object instanceof String) {
-			author = (String) ((JSONObject) info.get(AUTHORS)).get(AUTHOR);
-			System.out.println("- Author: ");
-			System.out.println(author);
-			authorsArray = new ArrayList<Object>();
-			authorsArray.add(author);
-			tuple = new Object[] {authorsArray, title, url, year, venue, type, key};
-		}
-		
-		System.out.print("- Venue: ");
-		System.out.println(venue);
-		System.out.print("- Year: ");
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorsPublicationsSearch.java

@@ -1,40 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.search;
-
-import java.util.ArrayList;
-import java.util.Scanner;
-
-import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
-import inesc_id.gsd.bibtrek.app.dblp.parsing.AuthorJSONParser;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.AuthorsPublicationsSearchBranch;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
-
-public class AuthorsPublicationsSearch {;
-	
-	private String choice;
-	private DBLPQueryCreator queryCreator; 
-	private Scanner userInput;	
-	
-	
-	public AuthorsPublicationsSearch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {
-		this.queryCreator = queryCreator;
-		this.userInput = userInput;
-		this.choice = choice;
-	}
-
-	public void search(ArrayList<Object[]> tupleArrayList) throws AuthorsPublicationsSearchException {		
-		AuthorsPublicationsSearchBranch authorsPublicationsSearchBranch;										
-
-		if(!tupleArrayList.isEmpty()) {			
-			try {											
-				authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.queryCreator, this.userInput, this.choice);
-				authorsPublicationsSearchBranch.choose(tupleArrayList);
-			} catch (PublicationSearchException pse) {
-				throw new AuthorsPublicationsSearchException("search(): could not search for publication.");
-			}			
-		}		
-	}
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/PublicationSearch.java

@@ -1,90 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.search;
-
-import java.util.ArrayList;
-import java.util.Scanner;
-
-import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
-import inesc_id.gsd.bibtrek.app.dblp.parsing.PublicationJSONParser;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.SearchBranch;
-
-public class PublicationSearch extends Search {
-	
-	private String choice;
-	private DBLPQueryCreator queryCreator; 
-	private Scanner userInput;	
-	
-	public PublicationSearch(DBLPQueryCreator queryCreator, Scanner userInput, String choice) {		
-		this.queryCreator = queryCreator;
-		this.userInput = userInput;
-		this.choice = choice;
-	}
-
-	@Override
-	public ArrayList<Object[]> search() throws PublicationSearchException {
-		String query, userChoice, getRequest;		
-		PublicationJSONParser publicationJSONParser;	
-		ArrayList<Object[]> tupleArrayList = null;
-		SearchBranch searchBranch;
-				
-		publicationJSONParser = new PublicationJSONParser();
-		searchBranch = new SearchBranch(this.choice, this.userInput);
-		
-		System.out.print("Type the publication's title: ");
-				
-		userChoice = this.userInput.nextLine(); 
-				
-		query = queryCreator.searchForPublication(userChoice);		
-		
-		try {
-			getRequest = this.executeQuery(query);
-		} catch (SearchException se) {
-			throw new PublicationSearchException("search(): could not execute the query: \"" + query + "\".");
-		}
-		publicationJSONParser.setString(getRequest);
-		System.out.println("");
-		System.out.println("(*) Publications Found: ");
-		tupleArrayList = publicationJSONParser.parseString();
-		if(!tupleArrayList.isEmpty()) {					
-			try {
-				searchBranch.choose(tupleArrayList);
-			} catch (SearchBranchException sbe) {
-				throw new PublicationSearchException("search(): could not search for publication.");
-			}			
-		}
-		
-		return tupleArrayList;
-	}
-	
-	public void search(String title) throws PublicationSearchException {
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/Search.java

@@ -1,30 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.search;
-
-import java.util.ArrayList;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchException;
-import inesc_id.gsd.bibtrek.app.dblp.search.condition.WriteConditionFactory;
-import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.exceptions.HTTPClientException;
-import inesc_id.gsd.bibtrek.app.http.HTTPClient;
-
-public abstract class Search {
-	
-	public Search() {
-	}
-	
-	public String executeQuery(String query) throws SearchException {
-		HTTPClient httpClient = new HTTPClient();
-		String getRequest;
-		try {
-			getRequest = httpClient.getRequest(query);
-			return getRequest;
-		} catch(HTTPClientException httpce) {
-			throw new SearchException("executeQuery(): could not execute a get request for"
-					+ " the website with url: \"" + query + "\".");
-		}
-	}
-		
-	public abstract ArrayList<Object[]> search() throws Exception;
-
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/condition/SearchBranch.java

@@ -1,112 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.search.condition;
-
-import java.util.ArrayList;
-import java.util.Scanner;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
-import inesc_id.gsd.bibtrek.app.dblp.writer.DBLPNoSQLWriter;
-import inesc_id.gsd.bibtrek.app.utils.StringToIntegerUtils;
-
-public class SearchBranch {
-	
-	private final static String AUTHOR = "author";
-	private final static String AUTHORS_PUBLICATIONS = "authors-publications";
-	private final static String PUBLICATION = "publication";
-	
-	private String choice;
-	private Scanner userInput;
-	
-	public SearchBranch(String choice, Scanner userInput) {
-		this.choice = choice;
-		this.userInput = userInput;
-	}
-	
-	@SuppressWarnings("unchecked")
-	public ArrayList<Object[]> choose(ArrayList<Object[]> tupleArrayList) throws SearchBranchException {
-		Object[] tuple;
-		String publicationChoice;
-		boolean exit = false;
-		
-		ArrayList<Object[]> addedPublications = new ArrayList<Object[]>();
-		while(true) {
-						
-			if(this.choice.equals(AUTHOR)) {
-				System.out.println("");			
-				System.out.println("(*) Author's Menu");
-			} else if(this.choice.equals(AUTHORS_PUBLICATIONS)) {
-				System.out.println("");
-				System.out.println("(*) Author's Publication Menu");
-			} else if(this.choice.equals(PUBLICATION)) {
-				System.out.println("");
-				System.out.println("(*) Publications Menu");
-			}
-			System.out.println("");
-			System.out.println("(a)");
-			System.out.println("- Add all of the available choices and exits the menu ; ");
-			System.out.println("");
-			System.out.println("(es)");
-			System.out.println("- Exits the choice menu and saves the configuration you have chosen ;");
-			System.out.println("");
-			System.out.println("(e!)");
-			System.out.println("- Exits the choice menu without saving ;");
-			System.out.println(""); 
-			System.out.print("Pick one of the publications to insert in the database: ");	            									
-			publicationChoice = this.userInput.nextLine();
-
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/AuthorDBLPNoSQLWriter.java

@@ -1,46 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.writer;
-
-import java.io.BufferedWriter;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.Iterator;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
-
-public class AuthorDBLPNoSQLWriter extends DBLPNoSQLWriter{
-	
-	public AuthorDBLPNoSQLWriter(ArrayList<Object[]> listToWrite) {
-		super(listToWrite);
-	}
-	
-	public synchronized void writeToFile() throws DBLPNoSQLWriterException {		
-		BufferedWriter bufferedWriter;
-		Iterator<Object[]> iter;
-		Object[] tuple;
-		String author, url;
-		
-		iter = listToWrite.iterator();
-		
-		try {
-			bufferedWriter = new BufferedWriter(new FileWriter(getCurrentFile(), true));
-			
-			while(iter.hasNext()) {
-				tuple = iter.next();
-				author = (String) tuple[0];
-				url = (String) tuple[1];
-				bufferedWriter.append(TimeUtils.getCurrentTimeString() + ": ");
-				bufferedWriter.append("CREATE (" 
-						+ author.replaceAll(REPLACE_REGEX, "") + ":Author {name:\"" 
-						+ author + "\", url:\"" + url + "\"})");
-				
-				bufferedWriter.append("\n");												
-			}			
-			bufferedWriter.close();
-		} catch (IOException ioe) {
-			throw new DBLPNoSQLWriterException("writeToFile(): could not write to the current state.");
-		}
-		
-	}
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/writer/PublicationsDBLPNoSQLWriter.java

@@ -1,72 +1,0 @@
-package inesc_id.gsd.bibtrek.app.dblp.writer;
-
-import java.io.BufferedWriter;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.Iterator;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPNoSQLWriterException;
-import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
-
-public class PublicationsDBLPNoSQLWriter extends DBLPNoSQLWriter{
-	
-	public PublicationsDBLPNoSQLWriter(ArrayList<Object[]> listToWrite) {
-		super(listToWrite);
-	}
-	
-	@SuppressWarnings("unchecked")
-	public synchronized void writeToFile() throws DBLPNoSQLWriterException {
-		BufferedWriter bufferedWriter;
-		Iterator<Object[]> iter;
-		Object[] tuple;
-		ArrayList<String> authorsArrayList;
-		String author = "no_author", title, url, year, venue, type, key;
-		
-		iter = listToWrite.iterator();
-		authorsArrayList = new ArrayList<String>();
-		
-		try {
-			bufferedWriter = new BufferedWriter(new FileWriter(getCurrentFile(), true));
-			
-			while(iter.hasNext()) {
-				tuple = iter.next();
-				
-				bufferedWriter.append(TimeUtils.getCurrentTimeString() + ": ");				
-				
-				title = (String) tuple[1];
-				url = (String) tuple[2];
-				year = (String) tuple[3];
-				venue = (String) tuple[4];
-				type = (String) tuple[5];
-				key = (String) tuple[6];				
-				
-				bufferedWriter.append("CREATE (" + title.replaceAll(REPLACE_REGEX, "")
-						+ ":Publication {title:\"" + title 
-						+ "\", url:\"" + url + "\", year:\"" + (int) Integer.valueOf(year) 
-						+ "\", venue:\"" + venue + "\", type:\"" + type 
-						+ "\", key:\"" + key + "\"})");				
-				authorsArrayList = (ArrayList<String>) tuple[0];
-				for(String authorIter : authorsArrayList) {
-					author = authorIter;					
-					
-					bufferedWriter.append(" ");
-					
-					bufferedWriter.append("CREATE (" 
-							+ author.replaceAll("\\W", "") + ":Author {name:\"" + author + "\"})");
-					
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/exceptions/MainInterfaceException.java

@@ -1,11 +1,0 @@
-package inesc_id.gsd.bibtrek.app.exceptions;
-
-public class MainInterfaceException extends Exception {
-	
-	public MainInterfaceException(String errorMessage, Throwable err) {
-        super(errorMessage, err);
-    }
-    public MainInterfaceException(String errorMessage) {
-        super(errorMessage);
-    }
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/main/MainClass.java

@@ -1,26 +1,0 @@
-package inesc_id.gsd.bibtrek.app.main;
-
-import java.io.OutputStream;
-import java.io.PrintStream;
-
-import inesc_id.gsd.bibtrek.app.exceptions.MainClassException;
-import inesc_id.gsd.bibtrek.app.exceptions.MainInterfaceException;
-import inesc_id.gsd.bibtrek.app.neo4j.WriteNeo4JThread;
-
-public class MainClass {		
-	
-    public static void main(String[] args ) throws MainClassException {
-    	WriteNeo4JThread neo4JThread;
-		
-    	MainInterface mainInterface = MainInterface.getInstance();    	
-    	try {
-    		neo4JThread = new WriteNeo4JThread();
-    		//new Thread(neo4JThread).start();
-			mainInterface.display();
-		} catch (MainInterfaceException mie) {
-			throw new MainClassException("main(): an error occurred while displaying the menu! Aborting...");
-		}
-    }
-    
-
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/neo4j/WriteNeo4JThread.java

@@ -1,100 +1,0 @@
-package inesc_id.gsd.bibtrek.app.neo4j;
-
-import java.io.File;
-import java.util.ArrayList;
-
-import org.neo4j.driver.v1.exceptions.ServiceUnavailableException;
-
-import inesc_id.gsd.bibtrek.app.dblp.exceptions.DBLPConnectNeo4JException;
-import inesc_id.gsd.bibtrek.app.exceptions.WriteNeo4JThreadException;
-import inesc_id.gsd.bibtrek.app.utils.TimeUtils;
-
-public class WriteNeo4JThread implements Runnable {
-	
-	private final static String GET_FILE = "\\/.\\d*_\\d*.nosql";
-	
-	private final static String GRAPH_PASSWORD = "graph";
-	
-	private final static String NOSQL_PATH = "src/main/java/inesc_id/gsd/bibtrek/app/nosql/";
-	
-	private final static String PROCESSED = "processed";
-	private final static String PROCESSED_REGEX = ".*\\/processed";
-	
-	@Override
-	public void run() {				
-		try {
-			while(true) {
-				Thread.sleep(5*1000);
-				this.execute();
-			}
-		} catch (InterruptedException ie) {
-			System.out.println("run(): the writing thread was interrupted!");
-		} catch (WriteNeo4JThreadException wneo4jte) {
-			System.out.println(wneo4jte.getMessage());
-		}
-	}
-	
-	private void execute() throws WriteNeo4JThreadException {
-		File noSQLPath;
-		File[] listOfFiles;
-		ArrayList<String> fileNameArrayList = new ArrayList<String>();
-		
-		noSQLPath = new File(NOSQL_PATH);
-		listOfFiles = noSQLPath.listFiles();
-		
-		fileNameArrayList = this.recursiveDirectoryList(noSQLPath, listOfFiles, fileNameArrayList);
-		this.write(fileNameArrayList);				
-	}
-	
-	private ArrayList<String> recursiveDirectoryList(File path, File[] listOfFiles, ArrayList<String> fileNameArrayList) {
-		String fileName;
-		File newPath;
-		File[] newListOfFiles;
-		
-		for (int i = 0; i < listOfFiles.length; i++) {			
-			if (listOfFiles[i].isFile()) {
-				fileName = path + File.separator + listOfFiles[i].getName();
-				fileNameArrayList.add(fileName);				
-			} else if (listOfFiles[i].isDirectory() && !listOfFiles[i].toString().matches(PROCESSED_REGEX)) {				
[…]

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/sanitizer/QuerySanitizer.java

@@ -1,18 +1,0 @@
-package inesc_id.gsd.bibtrek.app.sanitizer;
-
-public abstract class QuerySanitizer {
-	
-	private String query; 
-	
-	public QuerySanitizer() {		
-	}
-	
-	public String sanitize() {
-		String sanitizedQuery;
-		
-		sanitizedQuery = query.replaceAll(" ", "");
-		
-		return sanitizedQuery;
-	}
-	
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/utils/StringToIntegerUtils.java

@@ -1,20 +1,0 @@
-package inesc_id.gsd.bibtrek.app.utils;
-
-public class StringToIntegerUtils {
-	
-	public static boolean isInteger(String string) {
-	    return isInteger(string,10);
-	}
-
-	public static boolean isInteger(String string, int radix) {
-	    if(string.isEmpty()) return false;
-	    for(int i = 0; i < string.length(); i++) {
-	        if(i == 0 && string.charAt(i) == '-') {
-	            if(string.length() == 1) return false;
-	            else continue;
-	        }
-	        if(Character.digit(string.charAt(i),radix) < 0) return false;
-	    }
-	    return true;
-	}
-}

### 2019-07-31 app/app/src/main/java/inesc_id/gsd/bibtrek/app/utils/TimeUtils.java

@@ -1,23 +1,0 @@
-package inesc_id.gsd.bibtrek.app.utils;
-
-import java.text.SimpleDateFormat;
-import java.util.Date;
-
-public class TimeUtils {
-	
-	private TimeUtils() {
-		
-	}
-	
-	public static String getCurrentTimeString() {
-		String dateString;
-		Date date;
-		SimpleDateFormat format;
-		
-		date = new Date();
-		format = new SimpleDateFormat("ddMMyyyy_HHmmssSSSSSS");	
-		dateString = format.format(date);
-		
-		return dateString;
-	}
-}

### 2019-07-31 app/src/main/java/inesc_id/gsd/bibtrek/app/dblp/search/AuthorsPublicationsSearch.java

@@ -4,6 +4,7 @@ import java.util.ArrayList;
 import java.util.Scanner;
 
 import inesc_id.gsd.bibtrek.app.dblp.DBLPQueryCreator;
+import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationSearchBranchException;
 import inesc_id.gsd.bibtrek.app.dblp.exceptions.AuthorsPublicationsSearchException;
 import inesc_id.gsd.bibtrek.app.dblp.exceptions.PublicationSearchException;
 import inesc_id.gsd.bibtrek.app.dblp.exceptions.SearchBranchException;
@@ -32,7 +33,7 @@ public class AuthorsPublicationsSearch {;
 			try {											
 				authorsPublicationsSearchBranch = new AuthorsPublicationsSearchBranch(this.queryCreator, this.userInput, this.choice);
 				authorsPublicationsSearchBranch.choose(tupleArrayList);
-			} catch (PublicationSearchException pse) {
+			} catch (AuthorsPublicationSearchBranchException apsbe) {
 				throw new AuthorsPublicationsSearchException("search(): could not search for publication.");
 			}			
 		}		

### 2019-08-26 article/article.tex
Artigo acabado

@@
 \begin{document}
-\title{\textbf{BibTrek: A Graph Visualization Tool for Cybersecurity Publications}}
+\title{\textbf{BibTrek: A Graph Visualization Tool for Cybersecurity Research Publications}}
 \date{}
-\author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico}
-\date{2019\\ July}
+\author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico, Universidade de Lisboa}
+\date{July \\2019}
 \maketitle
 
-\textbf{\textit{Abstract}--With the advent of bigger and more elaborate cyberattacks the search for hackers with a deep understanding of the most recent cutting-edge attacks is becoming more difficult.
-Since the information about these techniques is present in the most recent scientific research publications and because most of the knowledge present in them is built onto the work of several other publications, which they reference, we present BibTrek, a Graph Visualization Tool and Search Engine for Cybersecurity Papers, that intends to solve this exact problem.
+\textbf{\textit{Abstract}--With the advent of bigger and more elaborate cyberattacks, security researchers and operators are having difficulty in keeping up with the lasted research resuls.
+In many occasions, it is not trivial to discover the most important paper regarding one topic.
+Since the information about these techniques is usually present in scientific research publications and because most of the knowledge present in them builds on the work of several other publications, which they reference, to assist in this research and study endeavor, we propose BibTrek, a tool that can query bibliographic APIs and store data in a graph than can be visualized graphically.
 With BibTrek we shall make use of several computer science web-based libraries to acquire information from multiple sources and display them into a Neo4j graph database to better relate the references between publications, but also authors and other relevant information for the reader.
-We then present the implementation of a simple command line program that allows us to query the API of DBLP and select which information we shall include on our database.
-Finally, we talk about further considerations and engineering developments in order for BibTrek to provide a more complex and richer functioning yet providing an easy and enjoyable experience for the user.}
+We then present the implementation of a prototype that reads data from DBLP and stores the results in the Neo4J database.
+The code is available for testing and extension on GitHub.}
 
@@
 The number of cyberattacks is on the rise.
-The CVE statistics \cite{cvestatisticsbyyear} show a 21.56\% increase in the number of documented vulnerabilities over the past 19 years.
+The CVE statistics \cite{cvestatisticsbyyear} show an average increase of 21.56\% in the number of documented vulnerabilities over the past 19 years.
 With the amount of information available it is very easy for an ill-intentioned individual to carry out an attack and exploit some system with minimal computacional resources.
@@
 The techniques used to carry them out are are mostly found in blog posts and other social media with short publication times.
-However, for in-depth analysis and scientic rigour, there are scientific publications in peer-reviewed conferences and journals.
+However, for in-depth analysis and scientific rigour, there are scientific publications in peer-reviewed conferences and journals.
 Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past.
@@
 Usually the most cited papers are the most relevant regarding a certain subject.
-Having said that, the reality is that performing these kinds of bibliography surveys are time-consuming and inefficient, thus, creating the possibility of them being improved upon.
+Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient, thus, creating the possibility of them being improved upon.
 
@@
 With BibTrek we propose a graph visualization tool with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph.
-The use of this graph is therefore useful to relate the papers and their references making the workflow of the survey process more efficient.
-We implemented a tool prototype.
-It allows a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers therefore permitting an easy navigation of information.
+The use of this result is therefore useful to relate the papers and their references making the survey process more efficient.
+We implemented a tool prototype that allows a search from a set of either authors, publication titles or keywords dynamically producing a reference graph composed of the most relevant scientific papers allowing an easier navigation of information.
 
@@
 A simple example execution would follow these steps.
-Let us say we want to learn about the Spectre attack.
+Let us say we want to learn about the Spectre attack on microprocessors.
 We would choose the option to query one of the mentioned above libraries.
-Next, by selecting the option to search for a publication, we would then then type the word ``Spectre`` on the console terminal.
+Next, by selecting the option to search for a publication, we would then type the word ``Spectre'' on the console terminal.
 After choosing the Spectre publication, the paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
@@
 In section 5 we discuss further developments and upgrades to the application.
-Finally, in section 6 we present a brief conclusion of the work presented in the previous sections.
+Finally, in section 6 we present a brief conclusion of the work.
 \\[1\baselineskip]
@@
 \subsection{Design}
+To obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
+After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
+We present the results of the surveyed publicly-available bibliographic APIs in Table 1.
+The ``API'' column mentions if the library has an available API for the developer to use.
+``Crawlers'' is related with the permission for using a bot to crawl the information available in the webpage.
+Finally the ``Key'' column mentions the requirement of a special key to access the API.
+\\[1\baselineskip]
+Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j\cite{neo4j} graph database all the available hosted information about either publications, institutions, authors and subjects.
+This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.\\[1\baselineskip]
 The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems.
@@
 Finally, we use the java.net package in order to establish an HTTP connection with the DBLP API.
-\\[1\baselineskip]
-To obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
-After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
-We present the results of the surveyed publicly-available bibliographic APIs in Table 1.
-Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j\cite{neo4j} graph database all the available hosted information about either publications, institutions, authors and subjects.
-This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.
 
 \begin{table}[]
-\centering
-\captionof{\textbf{Table 1}}
+\captionof{\textbf{Table 1 - Publicly available bibliographic APIs}}
 \\[1\baselineskip]
@@
 
-\subsection{Implementation}
+\subsection{Operation}
 At the present time, BibTrek only uses the information obtained from querying DBLP API to populate our server.
-In the current implementation after choosing one of the available options to query the database, the user inputs either an author's name or publication title that is scanned and properly parsed into a query.
+In the current implementation after choosing one of the available options to query the database, the user inputs either an author's name or publication title that is  parsed into a query.
 Queries are done through the composition of a specifically formatted URL link and an HTTP request.
-After the query is successfully processed by the DBLP database the JSON response is properly parsed and displayed in the terminal console.
-After choosing whichever publications are appropriate for its research the parsed JSON response is transformed into a Cypher query and written into a file.
+After the query is successfully processed by the DBLP database the JSON response is parsed and displayed in the terminal console.
+Afterwards the user will choose from the available publications that were displayed on the console which are the ones that he would like to add to Neo4J database.
+These publications which are encoded in the JSON format are transformed into a Cypher query and written into a file.
 This file will later be used to create nodes and the relationships between them in our Neo4j database.
-This file is processed by a thread that periodically searches the current folder for newly written update files and is responsible for storing this information onto the graph database.
-Once the thread has finished its update responsibilities these files are then moved to a different folder in order not to be re-written into the database.
+This file is processed by a thread that periodically searches the current folder for newly written update files and is responsible for storing this information into the graph database.
+Once the thread has finished its update these files are then moved to a different folder not to be re-written into the database.
+\\[1\baselineskip]
 An example execution of a query would be the following.
@@
 After obtaining the HTTP response and parsing its JSON the information is then displayed to the user.
-Here, every available publication about the Spectre attack is shown on the console, in order for the user to choose one or more of them, therefore adding them to the Neo4j database.
+Here, all the found publications about the Spectre attack is shown on the console, for the user to choose one or more of them, adding them to the Neo4j database.
 Afterwards, the chosen information is then parsed into a Cypher query and stored.
@@
 In this section we discuss the tests that were done using the application to query a web based library and the parsing and processing of the results.
-Furthermore we elaborate on the functionalities present in BibTrek.
+Furthermore we elaborate on the functionalities present in the BibTrek prototype.
 Finally, we list the commands available on the program's terminal console.
@@
 Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
-\subsection{Functionalities}
-At the current moment we can choose only to retrieve data from the DBLP publication.
-Nonetheless, future versions will include an option to query the ArXiV library, IEEE Xplore and any combination of these.
-Choosing the DBLP option we are able to pick whichever option suits our interests the most.
-At the current time we are able to query by author's name, author's publications and publication title.
-Once queried, BibTrek presents us the data that it has been able to retrieve.
-The user is then given the option to mark whichever of the retrieved information will be stored in the Neo4j graph database.
-The marked options are then stored on the graph with their appropriate relations.
-It is possible at any given moment to cancel any of the above mentioned procedures.
 \subsection{Command-line interface}
-Here we present a detailed functioning of the interface. We elaborate on every avaible option for the user to interact with, and explain the way the system interacts with the web based library.
+Here we present a detailed functioning of the user interface. We show the available options for the user to interact with, and explain the way the system interacts with the web based library.
 \\[1\baselineskip]
@@
 We are then required to pick which of the displayed publications we want to add to our local database.
-\item \textbf{Query by author's publication}.
+\item \textbf{Query by author publications}.
 Similar to the first option, we type the author's name.
 BibTrek then fetches us all the available authors in the system.
-We are then asked to choose which of the fetched authors we want to search publications of.
+We are then asked to choose which of the retrieved authors we want to search publications of.
 After doing so, the system fetches us all the available publications for the chosen authors incrementally.
@@
 \end{itemize}
-It is worth mentioning that any given step of the above procedures we can choose either the option of adding all the displayed information to our data set or exit the current state of the system.
+Any given step of the above procedures we can choose either the option of adding all the displayed information to our data set or exit the current state of the system.
 
@@
 While Cross Ref does not visually represent its data, BibTrek does so using a graph database, also, differently to Cross Ref, is given to us the option to add user input publications that have been dynamically fetched from different libraries.\\[1\baselineskip]
-\textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} \cite{bookrecusingneo4j} is an application that using several books' BibTeX metadata and a Neo4j graph representation, through the use of user input Cypher queries, about either the author's name or book type, recommends us a book.
-Similarly to BibTrek, a Neo4j graph representation is used after parsing a book's metadata.
-The main difference being that BibTrek is focused around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
-Finally, BibTrek's Cypher queries are similarly done but to fetch the most referenced paper given a single author, keyword or publication title, making the scope different from book searching alone.\\[1\baselineskip]
 \textbf{VIS - Google Scholar Citation Visualisation} \cite{vis} is an application that is used to create a graph based on a geographic map that has information about a publication, for example, the place where it has been written, relating it, like BibTrek, through its references and citations with other publications all over the said map.
@@
 Finally, BibTrek is more versatile given the fact that it does not base its graph around a single publication, but every node that has been added to the system by the user so far.
+\\[1\baselineskip]
+\textbf{Book recommendation using Neo4j graph database in BibTeX book metadata} \cite{bookrecusingneo4j} is an application that uses BibTeX metadata from books to build a Neo4j graph representation, through the use of user input Cypher queries, about either the author's name or book type, can recommend books.
+Similarly to BibTrek, a Neo4j graph representation is used after parsing a book's metadata.
+The main difference compared to BibTrek is the focus around authors, keywords, publications and subjects whilst this application being focused exclusively on books.
+Finally, Cypher queries are similarly done but to fetch the most referenced paper given a single author, keyword or publication title, making the scope different from book searching alone.
 
@@
 Another key aspect to develop is the ability to infer better relations between the nodes already stored in the database.
-With this point in mind, we should use the node's URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each.
+With this point in mind, we could use the node's URL attribute to download the publication's PDF and use a text reading tool such as iText in order to read its references and through them relate which node references each.
 This way we can have a richer graph and understand which of the papers is the most important building block to learn about a certain subject.
@@
 Finally, we are not able to query our Neo4j graph database through the terminal console, apart from the example module, since there was not enough time to implement it in the current version of the system.
-The work to be done regarding this topic, is the development of the option of querying the database through a user input choice from a vast array of specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
-An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject or given the current paper title that references one of the said papers.
+The work to be done regarding this topic, is the development of querying the database through a user input choice from specific functions that manipulate the information present there, displaying relevant information about the current status of the data to the user we the intent on aiding its research process.
+An example of a query would be getting the most referenced paper by all the papers presently on the database with respect to a certain subject.
 
@@
 This paper describes the BibTrek prototype that was implemented.
-It allows us to fully query the DBLP database and acquire diverse information about the subject matter.
-Currently it presents a fully functional user interface allowing the user to insert all obtained information into the Neo4j graph database.
-We are able to construct a graph with some relevant node information.
-Namely authors and publications and the relations between them.
+It allows us to query the DBLP database and acquire diverse information.
+Currently it presents a functional user interface.
 BibTrek's main potential is the simplification of an exploratory bibliographic database to our advantage.
@@
 
-\section{Acknowledgements}
-The writer of this article would like to thank Professor Miguel L.
-Pardal and INESC-ID for having invited him for a one month summer-internship program and for the reviewing of this article.
-With this program the writer learned highly valuable knowledge in the areas of cybersecurity, distributed systems and scientific research from multiple researcher peers.
-Non only that but also acquired a greater work ethic.
-With this being said he has the utmost gratitude for having been part of this project from which he has learned immensely from.
+\section*{Acknowledgements}
+The writer of this article would like to thank Professor Miguel L. Pardal and INESC-ID for having invited him for a one month summer-internship program and for the reviewing of this article.
 

### 2020-01-23 article/article.tex
Final corrections to the article.tex

@@
 \date{}
-\author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico, Universidade de Lisboa}
-\date{July \\2019}
+\author{Jos\'{e} Eduardo Br\'{a}s\\Instituto Superior T\'{e}cnico, Universidade de Lisboa, Portugal}
+\date{July 2019}
 \maketitle
 
-\textbf{\textit{Abstract}--With the advent of bigger and more elaborate cyberattacks, security researchers and operators are having difficulty in keeping up with the lasted research resuls.
+\textbf{\textit{Abstract}--With the advent of more elaborate cyberattacks, security researchers and operators are having difficulty in keeping up with the lasted research results.
 In many occasions, it is not trivial to discover the most important paper regarding one topic.
-Since the information about these techniques is usually present in scientific research publications and because most of the knowledge present in them builds on the work of several other publications, which they reference, to assist in this research and study endeavor, we propose BibTrek, a tool that can query bibliographic APIs and store data in a graph than can be visualized graphically.
-With BibTrek we shall make use of several computer science web-based libraries to acquire information from multiple sources and display them into a Neo4j graph database to better relate the references between publications, but also authors and other relevant information for the reader.
-We then present the implementation of a prototype that reads data from DBLP and stores the results in the Neo4J database.
-The code is available for testing and extension on GitHub.}
+The technical information is usually present in scientific research publications and most of the knowledge present in them relies on the work of several other publications, which they reference.
+To assist in this research and study endeavor, we propose BibTrek, a tool that can query bibliographic APIs and store data in a graph than can be visualized.
+With BibTrek we make use of several computer science web-based libraries to acquire information from multiple sources and display them into a graph database to better relate the references between publications, but also authors and other relevant information.
+We present the implementation of a prototype that reads data from DBLP and stores the results in the Neo4J database.
+The code is available on GitHub.}
 
@@
 \\[1\baselineskip]
-As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart these kinds of attacks effectively.
-However, with the increased availability of information on the web it is becoming easier to study and learn how these attacks work.
+As a result of the rising number of cyberattacks, it is becoming hard to find white-hat hackers that know how to thwart attacks effectively.
+However, with the increased availability of information on the web it is becoming easier to study and learn how attacks work.
 The techniques used to carry them out are are mostly found in blog posts and other social media with short publication times.
-However, for in-depth analysis and scientific rigour, there are scientific publications in peer-reviewed conferences and journals.
+However, for in-depth analysis and scientific rigour of fundamental problems, there are scientific publications in peer-reviewed conferences and journals.
 Due to the many iterations of scientific knowledge the most recent work builds upon the work that has been done on the past.
@@
 Usually the most cited papers are the most relevant regarding a certain subject.
-Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient, thus, creating the possibility of them being improved upon.
+Having said that, the reality is that performing these kinds of bibliography surveys is time-consuming and inefficient, thus, there is a opportunity for improvement.
 
@@
 The visualization of information using graphs has the potential to improve the learning process and the construction of conceptual mind maps that make it easier to retain information and relate it with other topics \cite{enhancinglearningwithvisualizationtechniques}.
-With BibTrek we propose a graph visualization tool with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative easy-to-browse graph.
+With BibTrek we propose a graph visualization tool with the goal of relating the many different research papers in the area of cybersecurity and presenting that in an informative and easy-to-browse graph.
 The use of this result is therefore useful to relate the papers and their references making the survey process more efficient.
@@
 A simple example execution would follow these steps.
-Let us say we want to learn about the Spectre attack on microprocessors.
+Let us say we want to learn about the \emph{Spectre} attack on microprocessors.
 We would choose the option to query one of the mentioned above libraries.
 Next, by selecting the option to search for a publication, we would then type the word ``Spectre'' on the console terminal.
-After choosing the Spectre publication, the paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
-After the fact, the user can simply watch the graph visualization created by BibTrek, this way finding which papers are the most referenced and therefore understand which shall be the one that he should tackle first.
+After choosing a publication, the paper its references, authors and its subject will be added to the database and related with the other papers that were previously added by the user.
+After the fact, the user can simply watch the graph visualization created by BibTrek, this way finding which papers are the most referenced and therefore understand which shall be the one that he should read first.
 
@@
 In section 4 we show related work from other authors.
-In section 5 we discuss further developments and upgrades to the application.
+In section 5 we discuss further developments to the application.
 Finally, in section 6 we present a brief conclusion of the work.
@@
 To obtain the required information to populate our graph database we make use of the APIs provided to us by the major computer science libraries that host scientific research publications.
-After researching what the appropriate libraries were given their terms of service and API functionalities we have chosen as our means of obtaining information the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
+After searching what the appropriate libraries were given their terms of service and API functionalities we have chosen the libraries of ArXiV, DBLP and IEEEXplore \cite{arxiv, dblp, ieeexplore}.
 We present the results of the surveyed publicly-available bibliographic APIs in Table 1.
-The ``API'' column mentions if the library has an available API for the developer to use.
 ``Crawlers'' is related with the permission for using a bot to crawl the information available in the webpage.
+The ``API'' column mentions if the library has an available remote invocation service for the developer to use.
 Finally the ``Key'' column mentions the requirement of a special key to access the API.
 \\[1\baselineskip]
-Our app is presented through a simple command line Java program that through the use of user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j\cite{neo4j} graph database all the available hosted information about either publications, institutions, authors and subjects.
-This graph database can also later be queried through the use of console commands to infer useful information about the state of the system.\\[1\baselineskip]
+Our app is presented through a simple command line Java program that receives user provided queries, crawls the libraries mentioned above using their APIs and adds to the Neo4j\cite{neo4j} graph database all the available information about either publications, institutions, authors and subjects.
+This graph database can also later be queried through the use of console commands to infer useful information about the bibliography.\\[1\baselineskip]
 The BibTrek application was written using the Java programming language mainly due to the fact that it is ubiquitous on modern-day computing systems.
@@
 The user starts by choosing the option to query the libraries for a publication by its title.
-Let us say he chose to query the system for publications about the Spectre attack.
+Let us say he chose to query the system for publications about the \emph{Spectre} attack.
 Because of this a query is properly formatted in the following way: \url{https://dblp.org/search/publ/api/?q=Spectre&format=json}.
@@
 
-\section{Evaluation}
-In this section we discuss the tests that were done using the application to query a web based library and the parsing and processing of the results.
-Furthermore we elaborate on the functionalities present in the BibTrek prototype.
-Finally, we list the commands available on the program's terminal console.
-
-\subsection{Tests}
-We have tested our application for a set of author and publication queries whilst locally running Neo4j using a computer with the following specs:
-\begin{itemize}
-\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
-\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
-\item \textbf{GPU:} Intel Mobile 4 Series Chipset
-\item \textbf{RAM:} 4096MB @ 1066Mhz 
-\end{itemize}
-BibTrek successfully processed and inserted all nodes and relations into the Neo4j database.
-We were able to search for any added data with ease.
-However, the data retrieved from the DBLP database might present a variable number of field attributes.
-Since we are following a fixed attribute structure for our node data, some of these fields are ignored.
-Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
 \subsection{Command-line interface}
-Here we present a detailed functioning of the user interface. We show the available options for the user to interact with, and explain the way the system interacts with the web based library.
+Here we present a more detailed functioning of the user interface. We show the available options for the user to interact with, and explain the way the system interacts with the web based library.
 \\[1\baselineskip]
@@
 Choosing it, we are required to type the name of the author we want to search.
-Afterwards BibTrek fetches us, all authors present in the DBLP database with a similar name to the one that we have inserted previously.
+Afterwards BibTrek fetches all authors present in the DBLP database with a similar name to the one that we have inserted previously.
 We are then told to pick which of the fetched authors we want to insert into the database.
@@
 Any given step of the above procedures we can choose either the option of adding all the displayed information to our data set or exit the current state of the system.
+
+\section{Evaluation}
+In this section we discuss the tests that were done using the application to query a web based library and the parsing and processing of the results.
+Furthermore we elaborate on the functionalities present in the BibTrek prototype.
+Finally, we list the commands available on the program's terminal console.
+
+\\[1\baselineskip]
+We have tested our application for a set of author and publication queries whilst locally running Neo4j using a computer with the following hardware specifications:
+\begin{itemize}
+\item \textbf{OS:} 64-bit Ubuntu 18.04.2 LTS GNU/Linux 
+\item \textbf{CPU:} Intel Core 2 Duo P8700 @ 2.534GHz 
+\item \textbf{GPU:} Intel Mobile 4 Series Chipset
+\item \textbf{RAM:} 4096MB @ 1066Mhz 
+\end{itemize}
+BibTrek successfully processed and inserted all nodes and relations into the Neo4j database.
+We were able to search for any added data with ease.
+However, the data retrieved from the DBLP database might present a variable number of field attributes.
+Since we are following a fixed attribute structure for our node data, some of these fields are ignored.
+Future versions should consider adding these fields dynamically, we further these considerations on the Future Work section of this article.
 
@@
 At the current moment only the DBLP is being used.
-Finally, while the ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers.
+The ArXiV API is free to use, IEEE Xplore requires the use of a key attributed to its developers, but should also be usable.
 Another aspect that should be considered is the use of dynamic attributes since, at the moment, any block of data that is fetched has some of its attributes unused because, we adhere to a fixed attribute schema when adding data to the database.
 In the current version the nodes being added to the database are either Authors or Publications.
-We should consider adding Companies, Foundations, Organizations, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the user.
+We should consider adding Companies, Universities and other Institutions that authors are or have been linked with in the past, Keywords/Subjects and any other relevant information for the user.
 The BibTrek data schema should be developed to be able to represent a ``union'' of the most popular bibliographic databases.
